Question
========

The following chunk summarizes the number of tropical storms that have achieved a certain status (e.g., hurricane, tropical depression, or tropical storm) as well the [category of severity of the storm](https://en.wikipedia.org/wiki/Tropical_cyclone#Classifications,_terminology,_and_naming). 

```{r, message=FALSE}
library(tidyverse)

storms_summary <- storms %>%
  group_by(status, category) %>%
  summarize(num_storms = n_distinct(name))

storms_summary
```

The two plots shown below show the same data. 
In the plot on the left, the area of the dots is proportional to the number of storms. 
In the plot on the right, the radius of the dots is proportional to the number of storms. 

```{r, fig.show='hold', out.width="50%"}
storm_plot <- ggplot(storms_summary, aes(x = status, y = category)) + 
  geom_point(aes(size = num_storms))

# left figure
storm_plot

# right figure
storm_plot + 
  scale_radius()
```

Which of the following statements are true? 

Answerlist
----------
* The figure on the left is more accurate, because the *area* of the dots is proportional to the number of storms. 
* The figure on the right is more accurate, because the *radius* of the dots is proportional to the number of storms. 
* The area of the dot representing tropical depressions of category -1 should be *almost* four times as big as the dot representing category 4 hurricanes. This is true in the figure on the left.
* The area of the dot representing tropical depressions of category -1 should be *almost* four times as big as the dot representing category 4 hurricanes. This is true in the figure on the right.
* The area of the dot representing tropical depressions of category -1 should be *more than* four times as big as the dot representing category 4 hurricanes. This is true in the figure on the left.
* The area of the dot representing tropical depressions of category -1 should be *more than* four times as big as the dot representing category 4 hurricanes. This is true in the figure on the right.


Solution
========

Answerlist
----------
* True.
* False.
* True.
* False. The dot is more than four times as big. 
* False. It should be almost four times as big. 
* False. It should be almost four times as big. 

Meta-information
================
extitle: Area
exsection: aesthetics
exname: aesthetics-area
extype: mchoice
exsolution: 101000
