Question
========

The following call to `skimr::skim()` displays summary statistics about the `species` variable in the `starwars` data frame. 

```{r, error=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)

starwars %>%
  skimr::skim(species)
```

Consider the following function definition, and subsequent call of that function. 

```{r}
summarize_species <- function(species = "Human") {
  starwars %>%
    filter(species == species) %>%
    summarize(
      num_people = n(),
      avg_height = mean(height, na.rm = TRUE)
    )
}

summarize_species("Wookiee")
```

The function does not throw an error, but does not return the intended results. 
We know the results are incorrect, because there not 83 [Wookiee](https://en.wikipedia.org/wiki/Wookiee)s in [*Star Wars*](https://en.wikipedia.org/wiki/Star_Wars). 

Which of the following causes the problem?  

Answerlist
----------
* Setting `species == species` in the call to `filter()` is problematic, because R cannot distinguish between the argument to our function named `species` and the variable in `starwars` named `species`. 
* There should be an extra set of parentheses around the call to `summarize()`. 
* The expression starting with `num_people` has to be on the same line as `summarize()`.
* You need to add a `return()` statement at the end of the function.
* There is no object called `starwars` in the global environment. 


Solution
========

Answerlist
----------
* True.
* False.
* False.
* False.
* False.

Meta-information
================
extitle: argument matching
exsection: function
exname: function-arg-matching
extype: schoice
exsolution: 10000
