Question
========

The `population` data frame contains three columns: `country`, `year`, and `population`.
The data encode each country's population over time. 

```{r, message=FALSE}
library(tidyverse)
population
```

The following function takes the name of a country as a `character` vector, and returns a one-row `tibble` with the entry in `population` corresponding to the year in which that country had its highest population. 

```{r}
max_pop <- function(country_name) {
  population %>%
    filter(country == country_name) %>%
    arrange(desc(population)) %>%
    head(1)
}
```

For example, according to these data the population of [Germany](https://en.wikipedia.org/wiki/Germany) peaked in 2004.

```{r}
max_pop("Germany")
```

Suppose that you want to retrieve the most populous years for the three countries stored in the `character` vector `my_countries`. 

```{r}
my_countries <- c("Germany", "Ghana", "Russian Federation", "United States of America")
```

Which of the following calls will **return a `tibble`**?

Answerlist
----------
* `map_dfr(my_countries, max_pop)`
* `map(my_countries, max_pop)`
* `map_chr(my_countries, max_pop)`
* `map2(my_countries, max_pop)`
* `map(.f = my_countries, max_pop)`

Solution
========

Answerlist
----------
* True.
* False. This will return a `list`.
* False. `max_pop()` does return a `character` vector.
* False. `map2()` requires three arguments. 
* False. `.f` should be the name of the function. 

Meta-information
================
exname: iteration-map-dfr
extype: schoice
exsolution: 10000
