Question
========

Consider the following list of names of countries. 

```{r, message=FALSE}
library(tidyverse)

my_countries <- c("Germany", "Ghana", "Russian Federation", "United States of America")
```

The `str_sub()` function returns a substring of a character vector, by starting at one location and continuing until some other location. 

For example, here we grab the first four characters of "We the people". 

```{r}
str_sub("We the people", start = 1, end = 4)
```

The following chunk attempts to extract the first three characters of each entry in the list of countries. 

```{r, error=TRUE}
map_int(my_countries, str_sub, start = 1, end = 3)
```

Why doesn't this work? 

Answerlist
----------
* Because `str_sub()` returns a `character` vector, but `map_int()` wants an `integer` vector. 
* Because `str_sub()` is not vectorized. 
* Because you need parentheses after `str_sub`. 
* Because you forgot to load the `tidyverse`.
* Because you forgot to load `purrr`. 

Solution
========

Answerlist
----------
* True.
* False. `str_sub()` is vectorized.
* False. You don't need parentheses after `str_sub`
* False. You did load the `tidyverse`.
* False. `purrr` is part of the `tidyverse`. 

Meta-information
================
extitle: map-error
exsection: iteration
exname: iteration-error
extype: schoice
exsolution: 10000
