Question
========

The `population` data frame contains three columns: `country`, `year`, and `population`.
The data encode each country's population over time. 

```{r, message=FALSE}
library(tidyverse)
population
```

The following chunk fits a [linear regression](https://en.wikipedia.org/wiki/Linear_regression) model for `population` as a function of `year` for each country separately. 

```{r, eval=FALSE}
population %>%
  group_by(country) %>%
  group_map(~lm(population ~ year, data = .))
```

Which of the following statements is **false**?

Answerlist
----------
* The first `~` (in the call to `group_map()`) tells R that what follows is an expression. 
* The second `~` (in the call to `lm()`) species the formula for the regression model. 
* This chunk returns a `list`, with each item being a regression model object. 
* The dot `.` refers to the `tibble` corresponding to each country. 
* Changing `group_map()` to `group_modify()` would produce the same result.

Solution
========

Answerlist
----------
* This statement is true.
* This statement is true.
* This statement is true.
* This statement is true.
* Correct. This statement is false.

Meta-information
================
extitle: group-map
exsection: iteration
exname: iteration-group-map
extype: schoice
exsolution: 00001
