Question
========

Consider the following list of names of countries. 

```{r, message=FALSE}
library(tidyverse)

my_countries <- c("Germany", "Ghana", "Russian Federation", "United States of America")
```

The following chunk shows two ways of counting the number of spaces (` `) in the name of each of our countries. 
The results are identical.

```{r}
str_count(my_countries, " ")
map_int(my_countries, str_count, " ")
```

Which method is more efficient (i.e., faster) and why? 

Answerlist
----------
* Using `str_count()` only is faster, because `str_count()` is vectorized. 
* Using `map_int()` is faster, because it causes a loop. 
* It doesn't matter -- the results are the same. 
* You could compute it even faster by using `lapply()` instead of `map_int()`. 

Solution
========

Answerlist
----------
* True.
* False. This way is slower because of the loop. 
* False. It matters and `str_count()` is faster. 
* False. `lapply()` and `map()` are basically the same and a vectorized function will be faster than both. 

Meta-information
================
exname: iteration-vectorized
extype: schoice
exsolution: 1000
