Question
========

The following chunk plots the path of [Hurricane Andrew](https://en.wikipedia.org/wiki/Hurricane_Andrew), which decimated the Bahamas, Florida, and the Gulf Coast in 1992. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
andrew <- storms %>%
  filter(year == 1992, name == "Andrew") %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(4326)
```

```{r}
library(leaflet)
leaflet() %>%
  addCircles(data = andrew)
```

The location of the points is correct, but there is no contextual information on the map to help us understand where Hurricane Andrew hit. 

What command would add this underlying contextual information to the map? 



Answerlist
----------
* `addTiles()`
* `addPolylines()`
* `addPolygons()`
* `addMapTiles()`
* `addContext()`
* `addMap()`


Solution
========

Answerlist
----------
* True.
* False. 
* False. 
* False. 
* False. 
* False. 


Meta-information
================
extitle: addTiles
exsection: leaflet
exname: leaflet-tiles
extype: schoice
exsolution: 100000
