Question
========

Consider the following choropleth of the population of the various United States. 
The color of each state corresponds to its population, as measured in 2015. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
library(usmap)

states <- us_map() %>%
  st_as_sf(coords = c("x", "y")) %>%
  st_set_crs(usmap_crs()) %>%
  group_by(group, full) %>%
  summarize(do_union = FALSE) %>%
  st_cast("POLYGON") %>%
  st_transform(4326) %>%
  left_join(statepop, by = "full")
```

```{r, error=TRUE, eval=TRUE}
library(leaflet)

pal <- colorBin(
  palette = "YlGnBu", 
  domain = states$pop_2015, 
  bins = c(0, 1e6, 5e6, 1e7, 3e7, Inf)
)

leaflet(states) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(pop_2015), 
    fillOpacity = 0.5, 
    weight = 0.3
  ) %>%
  addLegend("bottomleft", pal = pal, values = ~pop_2015)
```

Suppose that you did not like this particular set of colors. 
How could you change the plot to use a different set of colors? 

Answerlist
----------
* change the `palette` argument to `colorBin()`.
* change the `fillColor` argument to `addPolygons()`. 
* change the `values` argument to `addLegend()`.
* change the `fillOpacity` argument to `addPolygons()`.
* change the `domain` argument to `colorBin()`.

Solution
========

Answerlist
----------
* True.
* False. This would alter the appearance of the states, but not change the set of colors. 
* False. This would change the legend, but not the colors of the states. 
* False. This would change the shading of the states, but not the set of colors.
* False. This would change the mapping of colors to population values, but not the set of colors. 


Meta-information
================
extitle: choropleth
exsection: leaflet
exname: leaflet-choropleth
extype: schoice
exsolution: 10000
