Question
========

The following chunk isolates the path of tropical storms that hit during 1992. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
storms92 <- storms %>%
  filter(year == 1992) %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(4326)
```

The following chunk attempts to map the paths of these tropical storms over time to color, but throws an error. 

```{r, error=TRUE}
library(leaflet)

pal <- colorNumeric(palette = "Set2", domain = storms92$name)

leaflet(storms92) %>%
  addTiles() %>%
  addCircles(color = ~pal(name)) %>%
  addLegend(pal = pal, values = ~name, opacity = 0.8)
```

How can you fix the problem? 


Answerlist
----------
* It should be `color = pal(name)`.
* It should be `color = ~name`.
* It should be `fill = ~pal(name)`.
* It should be `aes(color = name)`.
* It should be `colorFactor` instead of `colorNumeric`.


Solution
========

Answerlist
----------
* False.  
* False. 
* False.
* False. That's `ggplot` syntax. 
* True.


Meta-information
================
extitle: categorical color mapping
exsection: leaflet
exname: leaflet-color-categorical
extype: schoice
exsolution: 00001
