Question
========

The following chunk attempts to plot the path of [Hurricane Andrew](https://en.wikipedia.org/wiki/Hurricane_Andrew), which decimated the Bahamas, Florida, and the Gulf Coast in 1992. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
andrew <- storms %>%
  filter(year == 1992, name == "Andrew") %>%
  select(name, lat, long) %>%
  st_as_sf(coords = c("lat", "long")) %>%
  st_set_crs(4326)
andrew
```

```{r}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addCircles(data = andrew)
```

The points appear to be south of Africa and even over [Antarctica](https://en.wikipedia.org/wiki/Antarctica). 
This is not even close to [Florida](https://en.wikipedia.org/wiki/Florida). 

What went wrong? 



Answerlist
----------
* In the `coords` argument, `lat` and `long` are in the wrong order. 
* The [CRS](https://en.wikipedia.org/wiki/Spatial_reference_system) is wrong -- it shouldn't be 4326. 
* The data in `storms` is not accurate. 
* It should be `addPolylines()` instead of `addCircles()`.
* The OpenStreetMap data is out-of-date. 


Solution
========

Answerlist
----------
* True.
* False. 4326 is the correct CRS.
* False. The data is accurate. 
* False. `addPolylines()` will throw an error. 
* False. The map data is accurate. 


Meta-information
================
extitle: switched lat and long
exsection: leaflet
exname: leaflet-latlong
extype: schoice
exsolution: 10000
