Question
========

The following chunk isolates the path of [Hurricane Andrew](https://en.wikipedia.org/wiki/Hurricane_Andrew), which decimated the Bahamas, Florida, and the Gulf Coast in 1992. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
andrew <- storms %>%
  mutate(timestamp = lubridate::parse_date_time(paste(year, month, day, hour), "%Y %m %d %H")) %>%
  filter(year == 1992, name == "Andrew") %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(4326)
```

The following chunk attempts to map the path of Hurricane Andrew over time to color, but throws an error. 

```{r, error=TRUE}
library(leaflet)

pal <- colorNumeric(palette = "Greens", domain = andrew$timestamp)

leaflet() %>%
  addTiles() %>%
  addCircles(data = andrew, color = pal(timestamp))
```

How can you fix the problem? 


Answerlist
----------
* It should be `color = ~pal(timestamp)`.
* It should be `color = ~timestamp`.
* It should be `fill = ~pal(timestamp)`.
* It should be `aes(color = timestamp)`.
* It should be `colorFactor` instead of `colorNumeric`.


Solution
========

Answerlist
----------
* True.
* False. You need the call to `pal()`. 
* False. The would create a plot, but the points wouldn't be colored. 
* False. That's `ggplot` syntax. 
* False. The variable we are mapping to color is continuous, not discrete. 


Meta-information
================
extitle: continuous color mapping
exsection: leaflet
exname: leaflet-color-continuous
extype: schoice
exsolution: 10000
