Question
========

The following chunk isolates the path of [Hurricane Andrew](https://en.wikipedia.org/wiki/Hurricane_Andrew), which decimated the Bahamas, Florida, and the Gulf Coast in 1992. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
andrew <- storms %>%
  mutate(timestamp = lubridate::parse_date_time(paste(year, month, day, hour), "%Y %m %d %H")) %>%
  filter(year == 1992, name == "Andrew") %>%
  st_as_sf(coords = c("long", "lat")) %>%
  st_set_crs(4326)
```

The following chunk attempts to plot the path of Hurricane Andrew by giving the user the ability to click on each dot and see the corresponding time stamp. 

```{r, error=TRUE, eval=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addCircles(data = andrew, ________ = ~timestamp)
```

What is the name of the missing argument?

Answerlist
----------
* `popup`
* `label`
* `text`
* `options`
* `marker`


Solution
========

Answerlist
----------
* True.
* True.
* False. 
* False. 
* False. 


Meta-information
================
extitle: popups
exsection: leaflet
exname: leaflet-popups
extype: mchoice
exsolution: 11000
