Question
========

Consider the following code chunk, which uses data from the `nycflights13` package about flights to and from three New York City airports in 2013. 

`ct_airports` is a `tibble` that contains only those airports that are in the [Central Time Zone](https://en.wikipedia.org/wiki/Central_Time_Zone). 

```{r, message=FALSE}
library(tidyverse)
library(nycflights13)
ct_airports <- airports %>%
  filter(tzone == "America/Chicago")

glimpse(ct_airports)
glimpse(flights)
nrow(flights)
nrow(ct_airports)
```

The result of the following chunk of code will be a `tibble` that contains how many rows? 

```{r, eval=FALSE}
flights %>%
  right_join(ct_airports, by = c("dest" = "faa"))
```


Answerlist
----------
* 342: one for each airport in `ct_airports`.
* 336,776: one for each flight in `flights`.
* less than 336,776, because only flights from New York City to airports in the Central Time Zone are included.
* more than 336,776, because each flights from New York City could have gone to multiple airports in the Central Time Zone. 

Solution
========

Answerlist
----------
* False.
* False.
* True.
* False.

Meta-information
================
exname: relational-multiplicity
extype: schoice
exsolution: 0010
