Question
========

The following code chunk creates a `tibble` called `drug_use_common` that records usage rates by age group for three commonly-used drugs (alcohol, marijuana, and cocaine). 

```{r, message=FALSE}
library(tidyverse)
library(fivethirtyeight)
drug_use_common <- drug_use %>%
  select(age, alcohol_use, marijuana_use, cocaine_use)
glimpse(drug_use_common)
```

We can use `ggplot()` to depict how alcohol usage changes with age. 

```{r}
ggplot(drug_use, aes(x = age, y = alcohol_use)) + 
  geom_col()
```

Suppose, however, that ultimately we want to produce the following plot? 

```{r, echo=FALSE} 
drug_use_alt <- drug_use_common %>%
  pivot_longer(-age, names_to = "drug", values_to = "usage_rate")
ggplot(drug_use_alt, aes(x = age, y = usage_rate, fill = drug)) + 
  geom_col()
```

What is the most efficient approach to producing our desired plot? 

Answerlist
----------
* Use `pivot_longer()` to stack the usage rates, set the `fill` aesthetic, and then draw the plot with a single call to `geom_col()`.
* Use `pivot_wider()` to stack the usage rates, set the `fill` aesthetic, and then draw the plot with a single call to `geom_col()`.
* Use `pivot_wider()` to spread out the usage rates, set the `color` aesthetic, and then draw the plot with a single call to `geom_col()`.
* Call `geom_col()` three times (once for each drug), and set the colors manually. 

Solution
========

Answerlist
----------
* True.
* False.
* False.
* False.

Meta-information
================
exname: reshape-ggplot
extype: schoice
exsolution: 1000
