Question
========

The `drug_use_young` data frame shown below contains 9 rows and 3 columns. It records drug usage rates among 12--14-year-olds. 

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(fivethirtyeight)
drug_use_young <- drug_use %>%
  filter(age < 15) %>%
  select(age, alcohol_use, marijuana_use, cocaine_use) %>%
  pivot_longer(-age, names_to = "drug", values_to = "usage_rate")
drug_use_young
```

The following application of `pivot_wider()` will result in a `tibble` with how many rows and columns? 

```{r, eval=FALSE}
drug_use_young %>%
  pivot_wider(names_from = drug, values_from = usage_rate)
```


Answerlist
----------
* 3 rows and 4 columns
* 3 rows and 3 columns
* 3 rows and 2 columns
* 6 rows and 3 columns
* 6 rows and 4 columns
* 9 rows and 3 columns
* 9 rows and 4 columns

Solution
========

Answerlist
----------
* True.
* False.
* False.
* False.
* False.
* False.
* False.

Meta-information
================
extitle: wider rows
exsection: reshape
exname: reshape-wider-rows
extype: schoice
exsolution: 1000000
