Question
========

The following code chunk creates a `tibble` called `drug_use_common` that records usage rates by age group for three commonly-used drugs (alcohol, marijuana, and cocaine). 

```{r, message=FALSE}
library(tidyverse)
library(fivethirtyeight)
drug_use_common <- drug_use %>%
  select(age, alcohol_use, marijuana_use, cocaine_use)
glimpse(drug_use_common)
```

A chunk of code here has been omitted. It contains call to a single function that converts `drug_use_common` to `drug_use_alt`. 

```{r, echo=FALSE} 
drug_use_alt <- drug_use_common %>%
  pivot_longer(-age, names_to = "drug", values_to = "usage_rate")
```

You can see what `drug_use_alt` looks like below. 

```{r}
glimpse(drug_use_alt)
```

Which function was called in the omitted chunk? 


Answerlist
----------
* `pivot_longer()`
* `pivot_wider()`
* `inner_join()`
* `filter()`
* `group_by()`
* `summarize()`

Solution
========

Answerlist
----------
* True.
* False.
* False.
* False.
* False.
* False.

Meta-information
================
exname: reshape-omitted
extype: schoice
exsolution: 100000
