Question
========
Consider the following R Markdown chunk:

```{r, error=TRUE, include=FALSE}
if ("package:tidyverse" %in% search()) {
  pkgs <- c(
    "package:tidyverse", "package:forcats", "package:stringr", 
    "package:dplyr", "package:purrr", "package:readr", 
    "package:tidyr", "package:tibble",  "package:ggplot2"
  )
  lapply(pkgs, detach, character.only = TRUE, unload = TRUE)
}
```

```{r}
library(tidyverse)
```

Adding which chunk option would result in the following output and the same effect?:

```{r, message=FALSE}
library(tidyverse)
```

Answerlist
----------
* `message = FALSE`
* `echo = FALSE`
* `warning = FALSE`
* `include = FALSE`
* `error = FALSE`
* `eval = FALSE`

Solution
========

Answerlist
----------
* True. 
* False. This suppresses the code in the chunk.
* False. This suppresses warning messages.
* False. This suppresses the output and the code.
* False. This allows knitting to continue even if there is an error in the chunk.
* False. This suppresses the evaluation of the code.

Meta-information
================
extitle: messages
exsection: rmarkdown
exname: rmarkdown-messages
extype: schoice
exsolution: 100000
