Question
========

The following chunk creates an `sf` object called `storms92` that contains data about tropical storms in 1992.
Data -- including location and atmospheric measurements -- were recorded every 6 hours. 
Thus, each observation (row) in this data frame represents a particular storm at a particular moment in time.

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
storms92 <- storms %>%
  filter(year == 1992) %>%
  st_as_sf(coords = c("long", "lat"))
storms92
```

The following chunk aggregates the data by storm, converts the resulting `MULTIPOINT` geometry into `LINESTRING`, computes the length of the path traveled by each storm, and then sorts the data frame in descending order by storm. 

```{r, eval=FALSE}
storms92 %>%
  group_by(name) %>%
  summarize(num_obs = n(), do_union = FALSE) %>%
  _________("LINESTRING") %>%
  mutate(distance = st_length(geometry)) %>%
  arrange(desc(distance))
```

A single function call is omitted. 
What is it? 

Answerlist
----------
* `st_cast()`
* `st_transform()`
* `st_combine()`
* `st_union()`
* `st_intersection()`

Solution
========

Answerlist
----------
* True.
* False. 
* False. 
* False. 
* False. 

Meta-information
================
extitle: cast
exsection: spatial
exname: spatial-cast
extype: schoice
exsolution: 10000
