Question
========

The following chunk creates an `sf` object called `storms92` that contains data about tropical storms in 1992.
Data -- including location and atmospheric measurements -- were recorded every 6 hours. 
Thus, each observation (row) in this data frame represents a particular storm at a particular moment in time.
Note that the geometry type here is `POINT`. 

```{r, message=FALSE, error=TRUE}
library(tidyverse)
library(sf)
storms92 <- storms %>%
  filter(year == 1992) %>%
  st_as_sf(coords = c("long", "lat"))

storms92
```

You want to aggregate these data by storm. 
The following output shows an `sf` object in which each row represents a single *storm*, with its geospatial coordinates having been aggregated.
Note that the geometry type here is `MULTIPOINT`. 

```{r, echo=FALSE, message=FALSE}
storms92 %>%
  group_by(name) %>%
  summarize(num_obs = n(), do_union = FALSE)
```

This computation was performed in a single chunk with a simple combination of operations. 
What combination of functions was used in the omitted chunk?  

Answerlist
----------
* `group_by() %>% summarize()`
* `group_by() %>% aggregate()`
* `group_by() %>% st_union()`
* `group_by() %>% st_combine()`
* `group_by() %>% st_intersection()`


Solution
========

Answerlist
----------
* True.
* False. 
* False. This would result in a `MULTIPOINT` geometry, but not an `sf` object.  
* False. This would result in a `MULTIPOINT` geometry, but not an `sf` object.  
* False. 

Meta-information
================
extitle: spatial aggregation
exsection: spatial
exname: spatial-aggregation
extype: schoice
exsolution: 10000
