---
chapter: "modeling"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-09-30 
version: 0.1
tags: [first, second, third]
id: ant-give-blanket
---

```{r ant-give-blanket-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Investigators in the HELP (Health Evaluation and Linkage to Primary Care) study were interested in modeling the probability of being `homeless` (one or more nights spent on the street or in a shelter in the past six months vs. housed) as a function of age.

a. Generate a confusion matrix for the null model and interpret the result.

 <!--begin-answer-->

XX NH
```{r }
library(mdsr)
```

 <!--end-answer-->
  
b. Fit and interpret logistic regression model for the probability of being `homeless` as a function of age. 

 <!--begin-answer-->

XX
```{r }
library(mdsr)
```

 <!--end-answer-->
  
  
c. What is the predicted probability of being homeless for a 20 year old?  For a 40 year old?

 <!--begin-answer-->

XX
```{r }
library(mdsr)
```

 <!--end-answer-->
 
 d. Generate a confusion matrix for the second model and interpret the result.


 <!--begin-answer-->

XX
```{r }
library(mdsr)
```

 <!--end-answer-->
  
  
