---
chapter: "spatial-II"
author: "mdsr1"
difficulty: "Medium"
date: 2020-06-24 
version: 0.1
tags: [violations, mapping]
id: ash-iron-painting
---

```{r ash-iron-painting-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
library(mdsr)
library(tidyr)
library(tidygeocoder)
library(ggspatial)
```


TITLE GOES HERE: The `Violations` data frame in the `r pkg_macro(mdsr)` package contains information on violations noted in Board of Health inspections of New York City restaurants. These data contain spatial information in the form of addresses and zip codes. 

a. Use the `geocode` function in `r pkg_macro(tidygeocoder)` to obtain spatial coordinates for these restaurants. 

 <!--begin-answer-->
```{r , message=FALSE}
library(tidygeocoder)
set.seed(1619)

addresses <- Violations %>%
  sample_n(5) %>%
  mutate(address = paste(street, ", NY", zipcode))

geocode(.tbl = addresses, address = address, method = "osm")
```
 <!--end-answer-->


b. Using the spatial coordinates you obtained in the previous exercise, create an informative static map using `r pkg_macro(ggspatial)` that illustrates the nature and extent of restaurant violations in New York City.

 <!--begin-answer-->
```{r,message=FALSE, warning = FALSE}
library(sf)
library(ggspatial)
library(tidygeocoder)

set.seed(23)
addresses <- Violations %>%
  sample_n(10) %>%
  mutate(address = paste(street, ", NY", zipcode))

addresses <- cbind(geocode(.tbl = addresses, address = address, method = "osm"))

addresses <- left_join(addresses, ViolationCodes, by = "violation_code")

address_sf <- addresses %>%
  filter(!is.na(lat)) %>%
  st_as_sf(coords = c("long", "lat"), crs = 4326)

ggplot() +
  annotation_map_tile(type = "osm") +
  geom_sf(data = address_sf, aes(color = critical_flag, size = score))
```

 <!--end-answer-->


c. Using the spatial coordinates you obtained in the previous exercises, create an informative interactive map using `leaflet` that illustrates the nature and extent of restaurant violations in New York City.

 <!--begin-answer-->

```{r}
library(leaflet)

leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = addresses %>% filter(long > -74, lat > 30, critical_flag == "Critical"), lng = ~long, lat = ~lat, popup = ~ paste("Restaurant Name : ", dba, "\n", " Violation: ", violation_description, "\n"), color = "red") %>%
  addCircleMarkers(data = addresses %>% filter(long > -74, lat > 30, critical_flag == "Not Critical"), lng = ~long, lat = ~lat, popup = ~ paste("Restaurant Name : ", dba, "\n", " Violation: ", violation_description, "\n"), color = "blue")
```

 <!--end-answer-->
