---
chapter: "modeling"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-09-30 
version: 0.1
tags: [first, second, third]
id: aspen-talk-ship
---

```{r aspen-talk-ship-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Investigators in the HELP (Health Evaluation and Linkage to Primary Care) study were interested in modeling associations between demographic factors and a baseline measure of depressive symptoms `cesd`.
They fit a linear regression model using the following predictors: `age`, `sex`, and `homeless` to the `HELPrct` data from the `r pkg_macro(mosaicData)` package.


a. Calculate and interpret the coefficient of determination ($R^2$) for this model and the null model.

 <!--begin-answer-->

XX

```{r message = FALSE}
library(mosaic)
rsquared(cesd_mod)
```

 <!--end-answer-->
 
b. Calculate and interpret the root mean squared error for this model and for the null model.

 <!--begin-answer-->

XX


 <!--end-answer-->
 
c. Calculate and interpret the mean absolute error (MAE) for this model and the null model.

 <!--begin-answer-->

XX

 <!--end-answer-->
  
  
  
