---
chapter: "modeling"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-09-30 
version: 0.1
tags: [depression, linear-regression]
id: aspen-talk-ship
---

```{r aspen-talk-ship-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Investigators in the HELP (Health Evaluation and Linkage to Primary Care) study were interested in modeling associations between demographic factors and a baseline measure of depressive symptoms `cesd`.
They fit a linear regression model using the following predictors: `age`, `sex`, and `homeless` to the `HELPrct` data from the `r pkg_macro(mosaicData)` package.


a. Calculate and interpret the coefficient of determination ($R^2$) for this model and the null model.

 <!--begin-answer-->

```{r message = FALSE}
library(mosaic)
cesd_mod <- lm(cesd ~ age + sex + homeless, data = HELPrct)
rsquared(cesd_mod)
```

The $R^2$ value is 0.04: only a small fraction of the variability in CESD scores is accounted for by the model.

 <!--end-answer-->
 
b. Calculate and interpret the root mean squared error for this model and for the null model.

 <!--begin-answer-->

```{r}
cesd_null <- lm(cesd ~ 1, data = HELPrct)
broom::glance(cesd_mod)
broom::glance(cesd_null)
```

The root mean squared error for the regression model is 12.3: this is interpreted loosely as the "average" deviation of the observed from the predicted.
The root mean squared error for the null model is 12.5.
This is not much larger (not surprising since the $R^2$ is so low).



 <!--end-answer-->
 
c. Calculate and interpret the mean absolute error (MAE) for this model and the null model.

 <!--begin-answer-->

```{r}
broom::augment(cesd_mod) |>
  mutate(ae = abs(cesd - .fitted)) |>
  summarize(mae = mean(ae))
broom::augment(cesd_null) |>
  mutate(ae = abs(cesd - .fitted)) |>
  summarize(mae = mean(ae))
```

The mean absolute error is 9.8 for the regression model: this increases to 10.1 for the null model.

 <!--end-answer-->
  
  
  
