---
chapter: "reproducible"
author: ""
difficulty: "Easy"
date: 2020-07-19 
version: 0.1
tags: [rmarkdown, errors]
id: bee-tell-roof
---

```{r bee-tell-roof-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Insert a chunk in an R Markdown document that generates an error.
Set the options so that the file renders even though there is an error.
(Note: Some errors are easier to diagnose if you can execute specific R statements during rendering and leave more evidence behind for forensic examination.)

 <!--begin-answer-->
Put this chunk
near the top of your R Markdown document if you want to soldier on through errors, i.e., turn foo.Rmd into foo.md and/or foo.html no matter what. 

``{r setup, include = FALSE, cache = FALSE}  
knitr::opts_chunk$set(error = TRUE)  
``

This is also helpful if you are writing a tutorial and want to demo code that throws an error. 
You might want to keep this as an RStudio snippet for easy insertion.

It's also possible to set things so that errors are tolerated in a
specific chunk.

```{r alwaysrun, error = TRUE}  
## code goes here
```

Use either of these strategies to 
generate an R Markdown file that includes an error but compiles nonetheless.  (Kudos to 
Jenny Bryan for describing this approach.)

 <!--end-answer-->
