---
chapter: "text"
author: ""
difficulty: "Easy"
date: 2020-06-14 
version: 0.1
tags: [macbeth, text, strings]
id: birch-write-shirt
---

```{r birch-write-shirt-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
library(mdsr)
```

TITLE GOES HERE: Use the `Macbeth_raw` data from the `r pkg_macro(mdsr)` package to answer the following questions: 


a. Speaking lines in Shakespeare's plays are identified by a line that starts with two spaces, then a string of capital letters and spaces (the character's name) followed by a period. Use `grep` to find all of the speaking lines in *Macbeth*. How many are there? 
 
<!--begin-answer-->
```{r}
data(Macbeth_raw)
macbeth <- strsplit(Macbeth_raw, "\r\n")[[1]]
speaker_lines <- macbeth[grep("^  [A-Z ]+\\.", macbeth)]
length(speaker_lines)
head(speaker_lines, 3)
```
Be careful: sometimes meta data can be interspersed with the results.
<!--end-answer-->

b.  Find all the hyphenated words in *Macbeth*.

<!--begin-answer-->
```{r}
data(Macbeth_raw)
lines <- strsplit(Macbeth_raw, "\r\n")[[1]]
words <- strsplit(paste(lines, collapse = " "), " ")[[1]]
grep("[a-z,A-Z]-[a-z,A-Z]", words, value = TRUE)
```
<!--end-answer-->
 
