---
chapter: "data-II"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-08-30 
version: 0.1
tags: [first, second, third]
id: birch-sell-bowl
---

```{r birch-sell-bowl-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: The `HELPfull` data within the `r pkg("mosaicData")` package contains information about the Health Evaluation and Linkage to Primary Care (HELP) randomized trial in *tall* format. 

a) Generate a table of the data for subjects (`ID`) 1, 2, and 3 that includes the `ID` variable, the `TIME` variable, and the `DRUGRISK` and `SEXRISK` variables (measures of drug and sex risk-taking behaviors, respectively).



<!--answer-start-->

```{r birch-sell-bowl-1}
library(mosaicData)
HELPfull %>%
  select(ID, TIME, DRUGRISK, SEXRISK) %>%
  filter(ID <= 3)
```

<!--answer-end-->

b) The HELP trial was designed to collect information at 0, 6, 12, 18, and 24 month intervals. At which timepoints were measurements available on the `*RISK` variables for subject 3?

<!--answer-start-->
The subject was observed at baseline, six months, and 24 months.
<!--answer-end-->

c) Let's restrict our attention to the data from the baseline (`TIME = 0`) and 6-month data.  Use the `pivot_wider()` function from the `r pkg("dplyr")` package to create a table that looks like the following:

```{r echo = FALSE}
HELPfull %>%
  select(ID, TIME, DRUGRISK, SEXRISK) %>%
  filter(ID <= 3, TIME < 12) %>%
  pivot_wider(
    id_cols = ID, 
    values_from = c(DRUGRISK, SEXRISK),
    names_from = TIME
  )
```

<!--answer-start-->
```{r echo = TRUE}
HELPfull %>%
  select(ID, TIME, DRUGRISK, SEXRISK) %>%
  filter(ID <= 3, TIME < 12) %>%
  pivot_wider(
    id_cols = ID, 
    values_from = c(DRUGRISK, SEXRISK),
    names_from = TIME
  )
```

<!--answer-end-->


d) Repeat this process using all subjects.  What is the Pearson correlation between  the baseline (`TIME = 0`) and 6-month `DRUGRISK` scores?  Repeat this for the `SEXRISK` scores. (Hint: use the `use = "complete.obs"` option from the `cor()` function.)

<!--answer-start-->

```{r echo = TRUE, message = FALSE}
HELPwide <- HELPfull %>%
  filter(TIME < 12) %>%
  pivot_wider(
    id_cols = ID, 
    values_from = c(DRUGRISK, SEXRISK),
    names_from = TIME
  )

HELPwide %>%
  summarize(
    drug_risk_cor = cor(DRUGRISK_0, DRUGRISK_6, use = "complete.obs"),
    sex_risk_cor = cor(SEXRISK_0, SEXRISK_6, use = "complete.obs")
  )
```
The Pearson correlation between the `DRUGRISK` variables is 0.60 while for the `SEXRISK` variables is 0.51. These are moderate associations.
<!--answer-end-->



