---
chapter: "algorithmic"
author: ""
difficulty: "Medium"
date: 2020-07-19 
version: 0.1
tags: [missing values, na, functions, mosaic, lahman]
id: bird-chew-dress
---

```{r bird-chew-dress-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: 

a. Write a function called `count_na` that, when given a vector as an argument, will count the number of `NA's` in that vector.  
Count the number of missing values in the `SEXRISK` variable in the `HELPfull` data frame in the `r pkg_macro(mosaicData)` package.

 <!--begin-answer-->
```{r }
library(tidyverse)
library(mosaicData)
count_na <- function(x) {
  return(sum(is.na(x)))
}

HELPfull %>%
  pull(SEXRISK) %>%
  count_na()

HELPfull %>%
  pull(SEXRISK) %>%
  summary()
```
  <!--end-answer-->

b. Apply `count_na` to the columns of the `Teams` data frame from the `r pkg_macro(Lahman)` package. 
How many of the columns have missing data?

 <!--begin-answer-->
```{r, message=FALSE}
library(Lahman)
missvars <- Teams %>%
  map_int(count_na)

mosaic::tally(~missvars)
missvars["SF"]
```
A total of `length(missvars)` columns have missing data. 
The `SF` column (denoting [sacrifice flies](https://en.wikipedia.org/wiki/Sacrifice_fly)) has the second most missing values (due to a relatively recent decision to record this statistic).
  <!--end-answer-->
