---
chapter: iteration
author: 'Nicholas Horton'
date: "First edition"
difficulty: Medium
version: 0.1
tags:
- HELPrct
- model fitting
- map
id: buck-lead-dish
output:
  pdf_document: default
---

(ref:buck-lead-dish) Exercise in file buck-lead-dish

```{r buck-lead-dish-default, include = FALSE}
mdsr2exercises::setup()
library(tidyverse)
library(mosaicData)
```

TITLE GOES HERE: Use the `purrr::map()` function and the `r mdsr2exercises::df_macro(HELPrct)` data frame from the `r mdsr2exercises::pkg_macro(mosaicData)` package to fit a regression model predicting `cesd` as a function of `age` separately for each of the levels of the `substance` variable.  Generate a table of results (estimates and confidence intervals) for the slope parameter for each level of the grouping variable.

<!--begin-answer-->

Use `group_by()` and `group_modify()` to fit the regression model on each part. Note that `broom::tidy()` is useful in having the output of the model be a data frame. 

```{r buck-lead-dish-1, echo = TRUE}
HELPrct %>%
  group_by(substance) %>%
  group_modify(
    ~broom::tidy(
      lm(cesd ~ age, data = .x), 
      conf.int = TRUE
    )
  ) %>%
  filter(term == "age")

```
<!--end-answer-->
