---
chapter: "regression"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [atus, linear regression]
id: cat-put-rug
---

```{r cat-put-rug-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `r pkg_macro(atus)` package includes data from the American Time Use Survey (ATUS).  Use the `atusresp` dataset to model `hourly_wage` as a function of other predictors in the dataset.

 <!--begin-answer-->

Answers may vary.  See the following for one possibility.
```{r warning=FALSE}
library(mosaic)
library(atus)
summary(atusresp)
```
```{r }
analysis <- filter(atusresp, !is.na(hourly_wage))
dim(analysis)
mod <- lm(hourly_wage ~ ptft + hh_child + ind_code,
  data = analysis
)
```
```{r }
anova(mod)
```
```{r }
msummary(mod)
```
```{r }
tally(~ind_code, data = analysis)
```
```{r moremplot}
mplot(mod, which = 2)
```
We see that (not surprisingly), part-time workers have significantly lower hourly wages than full time workers, and that not having a child is associated with an expected increase of \$0.16 (controlling for other factors).  Industry is a highly significant predictor (df=12, p$<$0.0001), with hospitality the lowest and public administration the highest.  The model explains 13.5% of the variability in hourly wages and the distribution of the residuals is highly skewed (long right tail since wage is a non-negative variable).  

<!--end-answer-->



