---
chapter: "join"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [baseball, lahman, dplyr]
id: cheetah-sit-car 
---

```{r cheetah-sit-car-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Use the `r df_macro(Batting)`, `r df_macro(Pitching)`, and `r df_macro(People)` tables in the `r pkg_macro(Lahman)` package to answer the following questions.

a. Name every player in baseball history who has accumulated at least 300 home runs (`r mdsr2exercises::var_macro(HR)`) and at least 300 stolen bases (`r mdsr2exercises::var_macro(SB)`). You can find the first and last name of the player in the `r df_macro(People)` data frame. Join this to your result along with the total home runs and total bases stolen for each of these elite players.

<!--begin-answer-->
```{r, message= FALSE, warning = FALSE}
library(Lahman)
Batting |>
  group_by(playerID) |>
  summarize(tHR = sum(HR), tSB = sum(SB)) |>
  filter(tHR >= 300 & tSB >= 300) |>
  left_join(People, by = c("playerID" = "playerID")) |>
  select(nameFirst, nameLast, tHR, tSB) |>
  arrange(desc(tHR))
```
<!--end-answer-->

b. Similarly, name every pitcher in baseball history who has accumulated at least 300 wins (`r mdsr2exercises::var_macro(W)`) and at least 3,000 strikeouts (`r mdsr2exercises::var_macro(SO)`).

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
Pitching |>
  group_by(playerID) |>
  summarize(tW = sum(W), tSO = sum(SO)) |>
  filter(tW >= 300 & tSO >= 3000) |>
  left_join(People, by = c("playerID" = "playerID")) |>
  select(nameFirst, nameLast, tW, tSO) |>
  arrange(desc(tSO))
```
<!--end-answer-->

c. Identify the name and year of every player who has hit at least 50 home runs in a single season. Which player had the lowest batting average in that season?

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
Batting |>
  group_by(playerID, yearID) |>
  summarize(tHR = sum(HR), BA = sum(H) / sum(AB)) |>
  filter(tHR >= 50) |>
  left_join(People, by = c("playerID" = "playerID")) |>
  select(nameFirst, nameLast, yearID, tHR, BA) |>
  ungroup() |>
  arrange(BA)
```
Jose Bautista had 54 homeruns in 2010, but had a batting average of only 0.260.
<!--end-answer-->
