---
chapter: "netsci"
author: "Ben Baumer"
difficulty: "Hard"
date: 2020-07-19 
version: 0.1
tags: [sql, imdb, igraph]
id: cheetah-dive-boat
---

```{r cheetah-dive-boat-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Let's reconsider the Internet Movie Database (IMDb) example.

a. In the `CROSS JOIN` query in the movies example, how could we have modified the SQL query to include the actor's and actresses' names in the original query? Why would this have been less efficient from a computational and data storage point of view? 


 <!--begin-answer-->
We could have joined onto the `names` table twice---once for the `src` actors and again for the `dest` actors. This would have been far less efficient, since `JOIN`s are big operations, and this would have resulting in the actors names being repeated in the data for each *edge*, as opposed to each *vertex*. 
  <!--end-answer-->

b. Expand the Hollywood network by going further back in time. If you go back to 2000, which actor/actress has the highest degree centrality? Betweenness centrality? Eigenvector centrality?

 <!--begin-answer-->

The following code should generate the graph, but we have suppressed the results here due to the time it takes to compile. 

```{sql, connection=mdsr::dbConnect_scidb("imdb"), output.var = "E"}
SELECT a.person_id as src, b.person_id as dest, 
  a.movie_id, 
  a.nr_order * b.nr_order as weight, 
  t.title, idx.info as ratings
  FROM imdb.cast_info a 
  CROSS JOIN imdb.cast_info b USING (movie_id)
  LEFT JOIN imdb.title t ON a.movie_id = t.id
  LEFT JOIN imdb.movie_info_idx idx ON idx.movie_id = a.movie_id
  WHERE t.production_year >= 2000 AND t.kind_id = 1
  AND info_type_id = 100 AND idx.info > 125000
  AND a.nr_order <= 20 AND b.nr_order <= 20
  AND a.role_id IN (1,2) AND b.role_id IN (1,2)
  AND a.person_id < b.person_id
  GROUP BY src, dest, movie_id
```

```{r}
E <- E %>%
mutate(ratings = as.numeric(ratings))
actor_ids <- unique(c(E$src, E$dest))
V <- mdsr::dbConnect_scidb("imdb") %>%
  tbl("name") %>%
  filter(id %in% actor_ids) %>%
  select(id, name) %>%
  rename(actor_name = name) %>%
  collect() %>%
  arrange(id)
```

```{r eval=FALSE}
library(igraph)
g <- graph_from_data_frame(E, directed = FALSE, vertices = V)

g <- g %>%
  set_vertex_attr("degree", value = degree(g)) %>%
  set_vertex_attr("eigen", value = eigen_centrality(g)$vector) %>%
  set_vertex_attr("pagerank", value = page_rank(g)$vector) %>%
  set_vertex_attr("btw", value = igraph::betweenness(g, normalized = TRUE))
get.data.frame(g, what = "vertices") %>%
  arrange(desc(btw)) %>%
  head()
```

  <!--end-answer-->

