---
chapter: "algorithmic"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2021-02-22 
version: 0.1
tags: [baseball, lahman, functions, onlineonly]
id: chicken-dream-kayak
---

```{r chicken-dream-kayak-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: 

a. Write a function called `group_consecutive()` that takes a vector of integers as input and returns a character string where the integers are sorted and consecutive values are listed with a `-` and other values separated by commas.
 
<!--begin-answer-->
```{r message=FALSE, warning = FALSE}
group_consecutive <- function(x) {
  # group consecutive values into a range, separate others by commas
  diffs <- diff(x)
  result <- as.character(x[1])
  pending <- FALSE
  for (i in 1:length(diffs)) {
    if (diffs[i] == 1) {
      pending <- TRUE   # move to the next one
    } else {
      if (pending) {   # process consecutive then new
        result <- paste0(result, "-", x[i], ", ", x[i+1])
        pending <- FALSE
      } else {  # pending was FALSE
        result <- paste0(result, ", ", x[i+1])
      }
    }
  }
  if (pending) {   # added this to solve issue with edge case
    result <- paste0(result, "-", x[length(x)])
  }
  return(result)
}
group_consecutive(c(1, 4, 5, 6, 7)) 
```
<!--end-answer-->

b. Use the function and the `Lahman` package to concisely list which seasons where Jim Bouton (author of *Ball Four*) played major league baseball.

<!--begin-answer-->
```{r}
library(Lahman)
bouton_years <-
  filter(Pitching, playerID == "boutoji01") |>
  arrange(yearID) |>
  select(yearID) |>
  unique() |>
  pull(yearID)
bouton_years
group_consecutive(bouton_years)
```

<!--end-answer-->


