---
chapter: "foundations"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [first, second, third]
id: chicken-draw-room
---

```{r chicken-draw-room-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Use the bootstrap to generate a 95% confidence interval for the regression parameters in 
a model for weight as a function of age for the `Gestation` data frame from the `r pkg_macro(mosaicData)` package.

 <!--begin-answer-->

```{r eval=TRUE, fig.height=3, fig.width=6, message=FALSE}
library(mosaicData)
mod <- lm(wt ~ age, data = Gestation)
coef(mod)
confint(mod)
```

```{r eval=TRUE, message=FALSE, error=TRUE}
library(rsample)
Gestation %>%
  bootstraps(times = 2000) %>%
  mutate(
    mod = map(splits, ~lm(wt ~ age, data = as_tibble(.x))),
    coefs = map(mod, coef),
    age = map_dbl(coefs, pluck, 2)
  ) %>%
  pull(age) %>%
  quantile(c(0.025, 0.5, 0.975))
```
For every year of age we would expect birth weight to increase by 0.1 ounces.
The bootstrap percentile method yields a similar interval.  We are 95% confident that the slope for age is between -0.09 and 0.29.  
  <!--end-answer-->


