---
chapter: "dataviz-III"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-08-16 
version: 0.1
tags: [weather, macleish, ggplot, visualization]
id: chicken-hurt-mug
---

```{r chicken-hurt-mug-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE:	The `r pkg_macro(macleish)` package contains weather data collected every 10 minutes in 2015 from two weather stations in Whately, Massachusetts.


Using the `r pkg_macro(ggplot2)` package, create a data graphic that displays the average temperature over each 10-minute interval (`temperature`) as a function of time (`when`) from the `whately_2015` dataframe. Create annotations to include context about the four seasons: the date of the vernal and autumnal equinoxes, and the summer and winter solstices.


<!--begin-answer-->
 
```{r message = FALSE}
library(macleish)
equinoxes <- tibble(
  Date = as.Date(c("2015-03-21", "2015-06-20", "2015-09-21", "2015-12-20")),
  season = c("Winter ", "Spring ", "Summer ", "Fall "))
whately_2015 <- whately_2015 |>
  mutate(Date = as.Date(when))
weather_plot <- ggplot(data = whately_2015,
  aes(x = Date, y = temperature)) +
  labs(y = "Temperature (degrees C)") + 
  geom_vline(data = equinoxes, color = "darkgray",
             aes(xintercept = as.numeric(Date))) +
  geom_text(data = equinoxes, aes(y = 33, label = season, hjust = "right")) +
  geom_line(size = 0.3, color = "darkgray") + geom_smooth() +
  scale_x_date()
weather_plot
```

<!--end-answer-->

 
 
