---
chapter: "spatial"
author: ""
difficulty: "Hard"
date: 2020-06-24 
version: 0.1
tags: [maps, airlines, dplyr, sf, ggspatial, onlineonly]
id: cow-take-bulb
---

```{r cow-take-bulb-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: 

a. Use the `airlines` data to make the airline route map for another carrier in another year. 

 <!--begin-answer-->

We will proceed to generate the network for US Airways (an airline that merged with American Airlines) in 2010.

```{r, warning=FALSE}
library(sf)
db <- dbConnect_scidb("airlines")
flights <- tbl(db, "flights")
carriers <- tbl(db, "carriers")
airports <- tbl(db, "airports")
```

```{r, warning=FALSE}
grabairline <- function(my_year = 2013, my_carrier = "DL") {
  flights %>%
    filter(year == my_year, carrier == my_carrier) %>%
    left_join(airports, by = c("dest" = "faa")) %>%
    group_by(dest) %>%
    summarize(
      N = n(), lon = max(lon), lat = max(lat),
      # note use of MySQL syntax instead of dplyr
      name = min(CONCAT(
        "(", dest, ") ",
        REPLACE(name, " Airport", "")
      ))
    ) %>%
    collect() %>%
    drop_na(lon, lat)
}
```

```{r usair, warning=FALSE}
usair2010 <- grabairline(my_year = 2010, my_carrier = "US") %>%
  st_as_sf(coords = c("lon", "lat")) %>%
  st_set_crs(4326)
glimpse(usair2010)
```


```{r usairmap, warning=FALSE, fig.height=10, fig.width=10, message = FALSE}
library(ggspatial)
route_map <- ggplot(usair2010) +
  annotation_map_tile() +
  geom_sf(alpha = 0.5, aes(size = N)) +
  scale_size()
route_map
```
 <!--end-answer-->


b. Compare the airline route map for Delta Airlines in 2017 to the same map for Delta in 2010. Discuss the history of Delta's use of hub airports. Quantify changes over time.  Reflect on the more general westward expansion of air travel in the United States. 

<!--begin-answer-->

We will use the tables and the `grabairline()` function from the previous 
problem.

```{r delta-years, warning=FALSE}
delta <- c(2017, 2010) %>%
  set_names() %>%
  map_dfr(grabairline, .id = "year") %>%
  arrange(year) %>%
  group_by(year) %>%
  mutate(prop = N / sum(N))
glimpse(delta)
```

```{r}
delta %>%
  group_by(year) %>%
  skimr::skim(prop)
```

```{r, message= FALSE}
changes <- delta %>%
  group_by(dest, lon, lat) %>%
  summarize(diff = diff(prop)) %>%
  st_as_sf(coords = c("lon", "lat")) %>%
  st_set_crs(4326)

changes %>%
  arrange(diff)

changes %>%
  arrange(desc(diff))
```

From 2010 to 2017, the proportion of Delta flights involving the Atlanta airport increased by 2.7\%, while the proportion involving Detroit decreased by 2.3\%.

The following figure displays the changes from 2010 to 2017.

```{r delta-map, warning=FALSE, fig.height=10, fig.width=10, message=FALSE}
library(ggspatial)
route_map <- ggplot(changes) +
  annotation_map_tile() +
  geom_sf(alpha = 0.5, aes(size = diff, color = diff)) +
  scale_size() + 
  scale_color_viridis_c()
route_map
```

```{r, include=FALSE}
DBI::dbDisconnect(db)
```


<!--end-answer-->

