---
chapter: "regression"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [linear regression, health, onlineonly]
id: cow-sing-dish
---

```{r cow-sing-dish-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: In the HELP (Health Evaluation and Linkage to Primary Care) study, investigators were interested in determining predictors of severe depressive symptoms (measured by the Center for Epidemiologic Studies---Depression scale, `cesd`) amongst a cohort enrolled at a substance abuse treatment facility. These predictors include `substance` of abuse (alcohol, cocaine, or heroin), `mcs` (a measure of mental well-being), gender, and housing status (housed or homeless). Answer the following questions regarding the following multiple regression model.

```{r message=FALSE, eval=TRUE, warning=FALSE}
library(mdsr)
fm <- lm(cesd ~ substance + mcs + sex + homeless, data = HELPrct)
msummary(fm)
confint(fm)
```

-  Write out the linear model.
-  Calculate the predicted CESD for a female homeless cocaine-involved subject with
an MCS score of 20.
-  Identify the null and alternative hypotheses for the 8 tests displayed above.

-  Interpret the 95% confidence interval for the `substancecocaine` coefficient.

-  Make a conclusion and summarize the results of a test of the `homeless` parameter.
-  Report and interpret the $R^2$ (coefficient of determination) for this model.
-  Which of the residual diagnostic plots are redundant?  
-  What do we conclude about the distribution of the residuals?
-  What do we conclude about the relationship between the fitted values and the residuals?
-  What do we conclude about the relationship between the MCS score and the residuals?
-  What other things can we learn from the residual diagnostics?
-  Which observations should we flag for further study?

 <!--begin-answer-->
-  We can calculate this quantity using the `makeFun()` function.
```{r }
fmfun <- makeFun(fm)
fmfun(substance = "cocaine", mcs = 20, sex = "female", homeless = "homeless")
```
The predicted CESD score given those factors is 41.4.

-  The linear model is given by:
$$E[CESD|X] = \beta_0 + \beta_1 COCAINE + \beta_2 HEROIN + \beta_3 MCS + \beta_4 MALE + \beta_5 HOUSED$$
where for example, $\beta_0=57.78$.

-  The 95% confidence interval for the `homeless` parameter (listed as `HOUSED` above) ranges from -2.54 to 0.87.  We are 95% confident that the true difference between housed and homeless subjects is in this range, after conditioning on the other factors in the model.

-  Since the p-value is large (0.34) and the 95% confidence interval includes 0, we conclude that after controlling for the other factors, housing status is not a significant predictor of CESD scores. 

```{r }
rsquared(fm)
```

The coefficient of determination ($R^2$) is 0.49: nearly half of the variability in CESD scores is explained by the predictors in the model.

-  We first generate a qqplot of the residuals (a histogram with superimposed normal curve might also be useful).

```{r foobl1, eval=TRUE}
mplot(fm, which = 2)
```

The distribution is approximately normal.  Some observations (e.g., 40, 351, and 433) have large residuals.

```{r foobl2}
mplot(fm, which = 1)
```

We see that there is some modest deviation from linearity (particularly in the tails).  The same observations are flagged.

We can add the residuals and fitted values into the dataframe, then generate the scatterplot with superimposed smoother.
```{r foobl3}
HELPrct <- HELPrct %>%
  mutate(resid = residuals(fm), fitted = fitted(fm))
ggplot(data = HELPrct, aes(x = mcs, y = resid)) +
  geom_point() +
  stat_smooth(method = lm) +
  stat_smooth(method = loess, color = "green") +
  ylab("Residuals") +
  xlab("MCS score")
```
The distribution is approximately linear.

Other residual plots are available by default.

```{r foobl4}
mplot(fm, which = 3)
```

The scale-location plot indicates that the assumption of homoscedasticity (equal variance) appears to be hold as a function of fitted values.

```{r foobl5}
mplot(fm, which = 4)
```

Three observations have extreme Cook's distance values.
```{r foobl6}
mplot(fm, which = 5)
```

The residuals versus leverage plot flags the same three points.

-  We see that four points might merit further scrutiny.
```{r }
HELPrct %>%
  select(cesd, fitted, resid, mcs, substance, mcs, sex) %>%
  slice(c(40, 351, 433, 450))
```

<!--end-answer-->


