---
chapter: "regression"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [linear regression, gestation, confidence intervals]
id: crocodile-toss-kayak
---

```{r crocodile-toss-kayak-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `Gestation` data set in `r pkg_macro(mdsr)` contains birth weight, date, and gestational period collected as part of the Child Health and Development Studies. Information about the baby's parents---age, education, height, weight, and whether the mother smoked is also recorded.

a. Fit a linear regression model for birthweight (`wt`) as a function of the mother's age (`age`).
b. Find a 95% confidence interval and p-value for the slope coefficient.
c. What do you conclude about the association between a mother's age and her baby's birthweight?


 <!--begin-answer-->

-  We can fit the model using the `lm()` function.

```{r}
mod <- lm(wt ~ age, data = Gestation)
msummary(mod)
confint(mod)
```

-  We observe a 95% confidence interval that ranges from -0.07 to 0.28 (associated p-value is 0.24).  
-  We conclude that there is not a statistically significant association between maternal age and child birth weight.  (However, other factors may be confounding this relationship.)

<!--end-answer-->


