---
chapter: data-I
author: "Daniel Kaplan"
date: '2019-10-24'
difficulty: Easy
version: 0.1
tags:
- babynames
- join
- dplyr
id: crow-burn-sheet
---

(ref:crow-burn-sheet) Exercise in file crow-burn-sheet

```{r crow-burn-sheet-default, include = FALSE}
mdsr2exercises::setup()
library(mdsr)
library(babynames)
library(tidyverse)
```

TITLE GOES HERE: Here is a random subset of the `babynames` data frame in the `r pkg_macro("babynames")` package:


```{r crow-burn-sheet-0, echo = FALSE}
set.seed(103)
Random_subset <- babynames %>%
  filter(n > 22) %>%
  sample_n(10)
```

```{r echo = TRUE}
Random_subset
```

For each of the following tables wrangled from `Random_subset`, figure out what `r pkg_macro(dplyr)` wrangling statement will produce the result.

a. Hint: Both rows and variables are missing from the original 

```{r echo = FALSE}
Random_subset %>%
  filter(n > 40, n < 100) %>%
  select(-prop)
```

<!--begin-answer-->
The `prop` column has been dropped, so we know there is a `select(-prop)` command in the wrangling statement. Also, all the rows with $n < 40$ and $n > 85$ have been dropped, meaning that there is also a `filter()` in the wrangling statement, perhaps `filter(n < 40, n > 85)`.
<!--end-answer-->

b. Hint: the `nchar()` function is used in the statement.
```{r echo = FALSE, message=FALSE}
Random_subset %>% filter(nchar(name) == 6)
```

<!--begin-answer-->
`nchar(name)` will calculate the number of letters in the `name` values. Both of the surviving rows have 6 letters. So a plausible wrangling statement is `filter(nchar(name) == 6)`.
<!--end-answer-->

c. Hint: Note the new column, which is constructed from `n` and `prop`.
```{r echo=FALSE, message=FALSE}
Random_subset %>%
  filter(year == 1989) %>%
  mutate(total = n / prop)
```

<!--begin-answer-->
First, the surviving rows are both for 1989, suggesting that `filter(year == 1989)` is part of the wrangling statement. Next, the `total` column has two numbers that are almost exactly the same and are in the millions. Could this be the total number of babies born in 1989? Try `mutate(total = n / prop)`.
<!--end-answer-->

d. Hint: All the years are still there, but there are only 8 rows as opposed to the original 10 rows.

```{r echo = FALSE, message=FALSE}
Random_subset %>%
  group_by(year) %>%
  summarize(total = sum(n))
```

<!--begin-answer-->
```{r, message=FALSE}
Random_subset %>%
  group_by(year) %>%
  summarize(total = sum(n))
```
<!--end-answer-->

