---
chapter: "simulation"
author: ""
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: dolphin-fight-pan
---

```{r dolphin-fight-pan-default, include = FALSE}
library(etude)
mdsr2exercises::setup()
```

TITLE GOES HERE:  Consider an example where a recording device that measures remote activity is placed in a remote location. The time, $T$, to failure of the remote device has an exponential distribution with mean of 3 years. Since the location is so remote, the device will not be monitored during its first 2 years of service. As a result, the time to
discovery of its failure is $X$ = max$(T, 2)$. The problem here is to determine the average of the time to discovery of the truncated variable (in probability parlance, the expected value of the observed variable $X$, E[X]).

The analytic solution is fairly straightforward but requires calculus. We need to evaluate:

$$E[X] = \int_0^{2} 2 f(u) du + \int_2^{\infty} u f(u) du,$$ where $f(u) = 1/3 \exp{(-1/3 u)}$ for $u > 0$.  
We can use the calculus functions in the `mosaicCalc` package to find the answer.

Is calculus strictly necessary here?
Conduct a simulation to estimate (or check) the value for the average time to discovery.

<!--begin-answer-->

Let's first find the analytic answer (though this is not required).
```{r, message = FALSE}
library(mosaicCalc)
library(mosaic)

options(digits = 6)
rate <- 1 / 3
F1 <- mosaicCalc::antiD((lambda * exp(-lambda * t)) ~ t, lambda = rate) # f(T)
F2 <- mosaicCalc::antiD((t * lambda * exp(-lambda * t)) ~ t, lambda = rate) # E[T]
2 * (F1(t = 2) - F1(t = 0)) + (F2(t = Inf) - F2(t = 2))
```

```{r echo=FALSE}
set.seed(1000)
```

```{r }
rate <- 1 / 3
numsim <- 100000
fail <- rexp(numsim, rate = rate)
# map all values less than 2 to be 2
fail[fail < 2] <- 2 # or mean(pmax(2, fail))
confint(t.test(fail))
```

We confirm that the mean time to discovery of failure is approximately 3.54 years.
<!--end-answer-->


