---
chapter: "dataviz-III"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-08-16 
version: 0.1
tags: [ggplot, themes]
id: dolphin-shut-shoe
---

```{r dolphin-shut-shoe-default, include = FALSE}
library(tidyverse)
library(mdsr)
library(mdsr2exercises)
mdsr2exercises::setup()
```

TITLE GOES HERE:	Create your own `r pkg_macro(ggplot2)` theme.  Describe the choices you made and justify why you made them using the principles introduced earlier.

<!--begin-answer-->

For example, here is the theme show in the book:

```{r}
mdsr::theme_mdsr
```

Many examples of other themes are found in various packages, most notably `r pkg_macro("ggthemes")`. 

```{r}
ggthemes::theme_economist
```

A custom theme can be created by writing a function that calls an existing theme, and simply makes some modifications to it. 

For example, the following function produces a theme that uses [Smith College's colors](https://www.smith.edu/about-smith/college-relations/brand-guidelines/fonts-colors) as facet labels. 

```{r}
theme_smith <- function() {
  ggplot2::theme_grey() %+replace%
    ggplot2::theme(
      strip.background = ggplot2::element_rect(
        fill = "#002855"
      ),
      strip.text = ggplot2::element_text(
        color = "#F2A900"
      )
    )
}

ggplot(mtcars, aes(x = disp, y = mpg)) + 
  geom_point() + 
  facet_wrap(~cyl) + 
  theme_smith()
```


<!--end-answer-->
