---
chapter: data-II
author: "Ben Baumer"
date: "First edition"
difficulty: Medium
version: 0.1
tags:
- dplyr
- pivot
- mistakes
id: eagle-dream-magnet
output: pdf_document
---


```{r eagle-dream-magnet-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: An analyst wants to calculate the pairwise differences between the Treatment and Control values for a small data set from a crossover trial (all subjects received both treatments) that
consists of the following observations.

```{r echo=FALSE, warning = FALSE}
library(xtable)
ds1 <- tibble(id = c(1:3, 1:3), group = c(rep("T", 3), rep("C", 3)), vals = c(4, 6, 8, 5, 6, 10))
```

```{r }
ds1
```

\vspace{.05in}

Then use the following code to create the new `diff` variable.

```{r eval=FALSE}
Treat <- filter(ds1, group == "T")
Control <- filter(ds1, group == "C")
all <- mutate(Treat, diff = Treat$vals - Control$vals)
all
```

Verify that this code works for this example and generates the correct values of $-1$, 0, and $-2$.  Describe two problems that might arise if the data set is not sorted in a particular
order or if one of the observations is missing for one of the subjects.  Provide an alternative approach to generate this
variable that is more robust (hint: use `pivot_wider`).

<!--begin-answer-->
Possible problems:

1. If the data are not in the same order within the two treatments, this approach will yield invalid results.
```{r echo=TRUE, message=FALSE, warning = FALSE}
ds2 <- tibble(
  id = c(1:3, 3:1),
  group = c(rep("T", 3), rep("C", 3)),
  vals = c(4, 6, 8, 10, 6, 5)
)
Treat <- filter(ds2, group == "T")
Control <- filter(ds2, group == "C")
all <- mutate(Treat, diff = Treat$vals - Control$vals)
all
```

2. If the data are not balanced (same number of observations for each of the new treatments) the code will yield a warning message.
```{r message=FALSE, warning = TRUE}
ds3 <- tibble(
  id = c(1:3, 1:2),
  group = c(rep("T", 3), rep("C", 2)),
  vals = c(4, 6, 8, 5, 6)
)
Treat <- filter(ds3, group == "T")
Control <- filter(ds3, group == "C")
all <- mutate(Treat, diff = Treat$vals - Control$vals)
all
```

We see that both examples yielded incorrect values (and one warning).

A better approach would be to use `pivot_wider()`.
```{r message=FALSE, warning = FALSE}
library(tidyr)
ds2 %>%
  pivot_wider(names_from = group, values_from = vals) %>%
  mutate(diff = T - C)
```

This approach yields the correct answer even though the data set is in a different order for the control observations.
<!--end-answer-->
