---
chapter: "data-I"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [baseball, lahman, dplyr]
id: eagle-grow-piano 
depends: kid-walk-chair
---

(ref:eagle-grow-piano) Exercise in file eagle-grow-piano

```{r eagle-grow-piano-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Using the `r df_macro(Teams)` data frame in the `r pkg_macro(Lahman)` package, display the top-5 teams ranked in terms of slugging percentage ($SLG$) in Major League Baseball history. Repeat this using teams since 1969. Slugging percentage is total bases divided by at-bats. To compute total bases, you get 1 for a single, 2 for a double, 3 for a triple, and 4 for a home run.

<!--begin-answer-->
```{r}
library(Lahman)
Teams <- mutate(Teams,
  SLG = (H + X2B + 2 * X3B + 3 * HR) / AB
)
Teams %>%
  select(yearID, teamID, lgID, SLG) %>%
  arrange(desc(SLG)) %>%
  head(5)
Teams %>%
  filter(yearID >= 1969) %>%
  select(yearID, teamID, lgID, SLG) %>%
  arrange(desc(SLG)) %>%
  head(5)
```
<!--end-answer-->


