---
chapter: "not working"
author: "Nicholas J. Horton"
difficulty: "Medium"
date: 2020-06-29 
version: 0.1
tags: [first, second, third, clickbait, text]
id: eagle-bet-boat
---

## Text

```{r eagle-bet-boat-default, include = FALSE}
mdsr2exercises::setup()
```


TITLE GOES HERE: 


Clickbait headlines are an all too common phenomenon in our everyday lives. The dataset `` from the `` package gives a sample of news headlines, some of which are considered clickbait and others not.

XX need to add in way to access articles

1. Identify any patterns or common words across articles that contain clickbait titles. 

  <!--begin-answer-->
```{r}
library(tidytext)

common_words <- articles %>%
  filter(clickbait == TRUE) %>%
  select(title) %>%
  unnest_tokens(text, title) %>%
  count(text, sort = TRUE)


common_bigrams <- articles %>%
  filter(clickbait == TRUE) %>%
  select(title) %>%
  unnest_tokens(text, title, token = "ngrams", n = 2) %>%
  count(text, sort = TRUE)
```
  <!--end-answer-->

2. Many articles that use clickbait typically have numbers in their titles (ex: "10 places you must visit..."). Find articles that have any numbers in the titles. 

  <!--begin-answer-->
```{r}
library(tidytext)
digits <- articles %>%
  filter(str_detect(articles$title, "^[[:digit:]]+"))

digits %>%
  count(clickbait)
```

  <!--end-answer-->


3. Find the number of words in each article. Is there any evidence to suggest that clickbait headlines are wordier?

  <!--begin-answer-->

```{r}
library(tidytext)
library(stringr)

num <- articles %>%
  mutate(len = (str_count(title, " ") + 1))

num.click <- num %>%
  filter(clickbait == TRUE) %>%
  mean(num.click$len)

num.not <- num %>%
  filter(clickbait == FALSE)

mean(num.not$len)
```

  <!--end-answer-->

4. Is there a relationship between the proportion of capital letters in a sentence and whether or not a headline has clickbait? Justify your answer. Hint: use the `words()` function to find the number of words in an article.  

  <!--begin-answer-->
```{r}
library(tidytext)

click.cap <- articles %>%
  filter(clickbait == TRUE) %>%
  mutate(ncap = str_count(title, pattern = "[A-Z]+"))
mean(click.cap$ncap)

not.click.cap <- articles %>%
  filter(clickbait == FALSE) %>%
  mutate(ncap = str_count(title, pattern = "[A-Z]+"))

mean(not.click.cap$ncap)
```
  <!--end-answer-->


5. Are clickbait headline articles more likely to have words with greater positive/negative sentiment?

```{r}

click <- articles %>%
  filter(clickbait == TRUE) %>%
  select(title) %>%
  unnest_tokens(text, title) %>%
  inner_join(get_sentiments("afinn"), by = c("text" = "word"))

not.click <- articles %>%
  filter(clickbait == FALSE) %>%
  select(title) %>%
  unnest_tokens(text, title) %>%
  inner_join(get_sentiments("afinn"), by = c("text" = "word"))

# add average values
```


