---
chapter: "reproducible"
author: ""
difficulty: "Medium"
date: 2020-07-19 
version: 0.1
tags: [code chunks, rmarkdown, formatting]
id: elephant-write-fork
---

```{r elephant-write-fork-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Explain what the following code chunks will display and why this might be useful for technical reports from a data science project.

````markdown
`r ''````{r chunk1, eval = TRUE, include = FALSE}
x <- 15
cat("assigning value to x.\n")
```
````

````markdown
`r ''````{r chunk2, eval = TRUE, include = FALSE}
x <- x + 3
cat("updating value of x.\n")
```
````

````markdown
`r ''````{r chunk3, eval = FALSE, include = TRUE}
cat("x =", x, "\n")
```
````

````markdown
`r ''````{r chunk1, eval = FALSE, include = TRUE}
```
````

````markdown
`r ''````{r chunk2, eval = FALSE, include = TRUE}
```
````

 <!--begin-answer-->

The first and second code chunk are run but not displayed until after the third chunk.
This might be useful to undertake some data wrangling in a report but defer the code display until the appendix.

```{r chunk1, eval = TRUE, include = FALSE}
x <- 15
cat("assigning value to x.\n")
```

```{r chunk2, eval = TRUE, include = FALSE}
x <- x + 3
cat("updating value of x.\n")
```

```{r chunk3}
cat("x =", x, "\n")
```


```{r chunk1, eval = FALSE, include = TRUE}
```

```{r chunk2, eval = FALSE, include = TRUE}
```

 <!--end-answer-->



