---
chapter: "data-I"
author: ""
date: "First edition"
version: 0.1
difficulty: "Medium"
tags: [baseball, second, third]
id: fir-pitch-fridge 
depends: kid-walk-chair
---

(ref:fir-pitch-fridge) Exercise in file fir-pitch-fridge

```{r fir-pitch-fridge-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Using the `r df_macro(Teams)` data frame in the `r pkg_macro(Lahman)` package:

a. Plot `r mdsr2exercises::var_macro(SLG)` versus `yearID` since 1954 conditioned by league (American vs. National, see `r mdsr2exercises::var_macro(lgID)`). Slugging percentage is total bases divided by at-bats. To compute total bases, you get 1 for a single, 2 for a double, 3 for a triple, and 4 for a home run.

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
library(Lahman)
Teams <- mutate(Teams,
  SLG = (H + X2B + 2 * X3B + 3 * HR) / AB
)
Teams %>%
  filter(yearID >= 1954) %>%
  ggplot(aes(x = yearID, y = SLG, color = lgID)) +
  geom_point(alpha = 0.5) +
  geom_smooth()
```
<!--end-answer-->

b. Is slugging percentage typically higher in the American League (AL) or the National League (NL)? Can you think of why this might be the case? 

<!--begin-answer-->  
The advent of the designated hitter (first added in the American League in 1973) seems to be associated with an increase in slugging percentage. 

<!--end-answer-->
