---
chapter: "netsci"
author: ""
difficulty: "Hard"
date: 2020-07-19 
version: 0.1
tags: [first, second, third]
id: fir-hold-clock
---

```{r fir-hold-clock-default, include = FALSE}
library(etude)
mdsr2exercises::setup()
```

TITLE GOES HERE: Use the `dbConnect_scidb` function to connect to the `airlines` database using the data from 2013 to answer the following problem.  For a while, [Edward Snowden](https://en.wikipedia.org/wiki/Edward_Snowden) was trapped in a Moscow airport. Suppose that you were trapped not in *one* airport, but in *all* airports. If you were forced to randomly fly around the United States, where would you be most likely to end up? 

<!--begin-answer-->

You'd be most likely to end up in Atlanta.

```{r message=FALSE, warning=FALSE}
library(mdsr)
library(DBI)
dbAir <- src_scidb("airlines")
E <- dbGetQuery(dbAir$con, "SELECT origin as src, dest, sum(1) as N
FROM flights WHERE year = 2012 GROUP BY origin, dest")

library(igraph)
g <- graph.data.frame(E, directed = TRUE)
E(g)$weight <- E(g)$N / sum(E(g)$N)

g <- g %>%
  set_vertex_attr("pagerank", value = page_rank(g)$vector)
get.data.frame(g, what = "vertices") %>%
  arrange(desc(pagerank)) %>%
  head()
```

  <!--end-answer-->


