---
chapter: "foundations"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [first, second, third]
id: fly-talk-boat
---

```{r fly-talk-boat-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `Whickham` data set in the `r pkg_macro(mosaicData)` package includes data on age, smoking, and mortality from a one-in-six survey of the electoral roll in Whickham, a mixed urban and rural district near Newcastle upon Tyne, in the United Kingdom. The survey was conducted in 1972--1974 to study heart disease and thyroid disease. A follow-up on those in the survey was conducted 20 years later. Describe the association between smoking status and mortality in this study.  Be sure to consider the role of age as a possible confounding factor.

 <!--begin-answer-->

We see that the risk of dying is lower for smokers than for non-smokers, since
31.4% of the non-smokers died, but only 23.9% of the smokers did not survive over the ten year period.
A graphical representation using a mosaicplot (also known as an *Eikosogram*) represents the cell
probabilities as a function of area.

```{r whick1}
library(mdsr)
library(mosaicData)
Whickham <- mutate(Whickham,
  agegrp = cut(age,
    breaks = c(1, 44, 64, 100),
    labels = c("18-44", "45-64", "65+")
  )
)
mosaicplot(mosaic::tally(~ outcome + smoker, data = Whickham),
  ylab = "Smoking status",
  xlab = "Mortality status (after 10 years)", main = "", color = TRUE
)
with(Whickham, gmodels::CrossTable(smoker, outcome,
  prop.c = FALSE, prop.chisq = FALSE,
  prop.t = FALSE
))
```

We note that the majority of subjects have survived, but that
the area for the smokers who are still alive is larger than we would expect if there were no
association between these variables.
What could explain this result?

Let's consider stratification by age of the participants.  The following displays describe the relationship
between smoking and mortality over a 10--year period for those age 18--44, those 45-64, and subjects that were 65 or older at baseline.


```{r whick2}
with(
  filter(Whickham, agegrp == "18-44"),
  gmodels::CrossTable(smoker, outcome, prop.c = FALSE, prop.chisq = FALSE, prop.t = FALSE)
)
mosaicplot(mosaic::tally(~ agegrp + outcome, data = Whickham),
  ylab = "mortality status (after 10 years)",
  xlab = "Age group", main = "", color = TRUE
)
with(Whickham, gmodels::CrossTable(agegrp, smoker,
  prop.c = FALSE, prop.chisq = FALSE,
  prop.t = FALSE
))
```

Not surprisingly, we see that
mortality rates are highest for the oldest subjects.
We also observe that
there is an association between age group and smoking status.

```{r whick3}
mosaicplot(mosaic::tally(~ agegrp + smoker, data = Whickham),
  ylab = "smoking status",
  xlab = "Age group", main = "", color = TRUE
)
```

Smoking is also associated with age, with those between
the ages of 45 to 64 most likely to have been smokers at baseline.


After controlling for age, smokers have a higher
rate of mortality than non-smokers in this study.


```{r whick4}
with(filter(Whickham, agegrp == "65+"), gmodels::CrossTable(smoker, outcome,
  prop.c = FALSE, prop.chisq = FALSE, prop.t = FALSE
))
```

The same is true for the other groups.
Simple methods such as stratification can allow analysts to think beyond two
dimensions and reveal effects of confounding variables.  
  <!--end-answer-->


