---
chapter: "data-I"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [baseball, lahman, dplyr, time-blocks]
id: fox-iron-sheet 
---

(ref:fox-iron-sheet) Exercise in file fox-iron-sheet

```{r fox-iron-sheet-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE:  Using the `r df_macro(Teams)` data frame in the `r pkg_macro(Lahman)` package:

a. Create a factor called `r mdsr2exercises::var_macro(election)` that divides the `r mdsr2exercises::var_macro(yearID)` into 4-year blocks that correspond to U.S. presidential terms. The first presidential term started in 1788. They each last 4 years and are still on the schedule set in 1788.

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
library(Lahman)
Teams %>%
  mutate(election = factor(cut(yearID,
    breaks = seq(from = 1788, to = 2017, by = 4)
  ))) %>%
  group_by(election) %>%
  summarize(N = n(), tHR = sum(HR)) %>%
  arrange(desc(tHR))
```
<!--end-answer-->

b. During which term have the most home runs been hit? -A- The interval from 2001--2004 (corresponding to George W. Bush's first term) was associated with the most homeruns.



