---
chapter: "appR"
author: ""
difficulty: "Medium"
date: 2020-07-15 
version: 0.1
tags: [first, second, third]
id: fox-write-bowl
---

```{r fox-write-bowl-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The following code undertakes some data analysis using the HELP (Health Evaluation and Linkage to Primary Care) trial.  

```{r eval=FALSE}
library(mosaic)
ds <-
  read.csv("http://nhorton.people.amherst.edu/r2/datasets/helpmiss.csv")
summarise(group_by(
  select(filter(mutate(ds,
    sex = ifelse(female == 1, "F", "M")
  ), !is.na(pcs)), age, pcs, sex),
  sex
), meanage = mean(age), meanpcs = mean(pcs), n = n())
```

Describe in words what computations are being done.
Using the pipe notation, translate this code into a more readable version.

<!--begin-answer-->
This code generates a new variable called `sex` based on the value of the `female` variable, drops any observations missing the `pcs` variable, selects three variables, then displays the average age, PCS, and sample size for each of the two groups defined by `sex`.

```{r eval=FALSE}
library(mosaic)
ds <-
  read.csv("http://nhorton.people.amherst.edu/r2/datasets/helpmiss.csv")
ds %>%
  mutate(sex = ifelse(female == 1, "F", "M")) %>%
  filter(!is.na(pcs)) %>%
  select(age, pcs, sex) %>%
  group_by(sex) %>%
  summarise(meanage = mean(age), meanpcs = mean(pcs), count = n())
```

Here it is much clearer what each operation within the "pipe-stream" is doing.  
It is straightforward to debug expressions in this manner by just leaving off the pipe operator at each line: this will only evaluate the set of functions called
to that point and display the intermediate output.

<!--end-answer-->


