---
chapter: dataviz-II
author: ''
difficulty: Medium
date: '2020-07-14'
version: 0.1
tags:
- first
- second
- third
id: giraffe-freeze-knife
output: pdf_document
---

```{r giraffe-freeze-knife-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `MLB_teams` data set in the `r pkg_macro(mdsr)` package contains information about Major League Baseball teams from 2008--2014. There are several quantitative and a few categorical variables present. See how many variables you can illustrate on a single plot in R. The current record is 7. (Note: This is *not* good graphical practice---it is merely an exercise to help you understand how to use visual cues and aesthetics!)


<!--begin-answer-->
```{r ggplotteamwin,fig.height=15, fig.width=10}
library(mdsr)
ggplot(MLB_teams) +
  geom_point(aes(
    x = payroll / 1000000, y = WPct, color = teamID,
    size = metroPop, shape = lgID, alpha = normAttend
  )) +
  facet_wrap(~yearID, ncol = 1) +
  xlab("Payroll (Millions of USD)") +
  ylab("Team Winning Percentage")
```
<!--end-answer-->


