---
chapter: "simulation"
author: ""
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [simulation, wait time, banks, onlineonly]
id: girl-run-scarf
---

```{r girl-run-scarf-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Consider a queuing example where customers arrive at a bank at a given minute past the hour and are served by the next available teller.  
Use the following data to explore wait times for a bank with one teller vs. one with two tellers, where the duration of the transaction is given below.

```{r echo=FALSE, results="asis"}
df <- tibble(
  arrival = c(1, 3, 7, 10, 11, 15), 
  duration = c(3, 2, 5, 6, 8, 1)
)
knitr::kable(df)
```
What is the average total time for customers in the bank with one teller?  What is the average for a bank with two tellers?


<!--begin-answer-->
For the bank with one teller the total times are 3, 3, 5, 8, 15, and 12 minutes (average of 7.7 minutes).
For the bank with two tellers the total times are 3, 2, 5, 6, 9, and 2 minutes (average of 4.5 minutes).
<!--end-answer-->


