---
chapter: spatial-I
author: ''
difficulty: Medium
date: '2020-06-25'
version: 0.1
tags:
- first
- second
- third
id: goat-ring-bottle
output: pdf_document
---


```{r goat-ring-bottle-default, include = FALSE}
mdsr2exercises::setup()
library(mdsr)
library(tidyverse)
library(pdxTrees)
library(leaflet)
```

TITLE GOES HERE: The `r pkg_macro(pdxTrees)` package contains a dataset of over 20,000 trees in Portland, Oregon, parks. 

a. Using `pdxTrees_parks` data, create a informative leaflet map for a tree enthusiast curious about the diversity and types of trees in the Portland area. 

<!--begin-answer-->

Using a random sample of 1,000 trees in the `pdxTrees_parks` dataset: 

```{r}
library(pdxTrees)
library(leaflet)
set.seed(3492)

pdxTrees_parks_sample <- get_pdxTrees_parks() %>%
  sample_n(1000) %>%
  janitor::clean_names()

pal <- colorFactor(
  palette = c("black", "orange", "dark green", "red"),
  domain = as.factor(pdxTrees_parks_sample$condition)
)

leaflet(pdxTrees_parks_sample) %>%
  addTiles() %>%
  addCircleMarkers(data = pdxTrees_parks_sample %>% filter(mature_size == "S"), group = "S", lng = ~longitude, lat = ~latitude, color = ~ pal(condition), radius = 5, popup = ~ paste(
    "Common Name: ", common_name, "Fun Fact: ",
    species_factoid, condition
  )) %>%
  addCircleMarkers(data = pdxTrees_parks_sample %>% filter(mature_size == "M"), group = "M", lng = ~longitude, lat = ~latitude, color = ~ pal(condition), radius = 5, popup = ~ paste(
    "Common Name: ", common_name, "Fun Fact: ",
    species_factoid
  )) %>%
  addCircleMarkers(data = pdxTrees_parks_sample %>% filter(mature_size == "L"), group = "L", lng = ~longitude, lat = ~latitude, color = ~ pal(condition), radius = 5, popup = ~ paste(
    "Common Name: ", common_name, "Fun Fact: ",
    species_factoid
  )) %>%
  addLayersControl(
    baseGroups = c("S", "M", "L"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addLegend(pal = pal, values = ~condition, opacity = 1)
```
  <!--end-answer-->

b. Not all trees were created equal. Create an  interactive map that highlights trees in terms of their overall contribution to sustainability and value to the Portland community using variables such as `carbon_storage_value` and `total_annual_benefits`, etc.

<!--begin-answer-->
```{r}
library(pdxTrees)
library(leaflet)

pal.eco <- colorBin(
  palette = "Greens",
  domain = pdxTrees_parks_sample$structural_value,
  bins = 5
)

leaflet(pdxTrees_parks_sample) %>%
  addTiles() %>%
  addCircleMarkers(data = pdxTrees_parks_sample %>% filter(native == "Yes"), group = "Native", lng = ~longitude, lat = ~latitude, color = ~ pal.eco(structural_value), radius = 5, popup = ~ paste("Common Name: ", common_name, "Carbon Sequestration in lbs: ", carbon_sequestration_lb)) %>%
  addCircleMarkers(data = pdxTrees_parks_sample %>% filter(native == "No"), group = "Non-Native", lng = ~longitude, lat = ~latitude, color = ~ pal.eco(structural_value), radius = 5, popup = ~ paste("Common Name: ", common_name, "Carbon Sequestration in lbs: ", carbon_sequestration_lb)) %>%
  addLayersControl(
    baseGroups = c("Native", "Non-Native"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addLegend(
    pal = pal.eco, values = ~structural_value, opacity = 1,
    title = "Structural Value", labFormat = labelFormat(prefix = "$")
  )
```
  <!--end-answer-->

c. Create an interactive map that helps identify any problematic trees that city officials should take note of. 

  <!--begin-answer-->
```{r, eval=FALSE, cache=TRUE}
library(pdxTrees)
library(leaflet)

leaflet(pdxTrees_parks_sample %>% filter(condition == c("Poor", "Dead"))) %>%
  addTiles() %>%
  addMarkers(data = pdxTrees_parks_sample %>% filter(!is.na(nuisance)), group = "Nuisance", lng = ~longitude, lat = ~latitude, popup = ~ paste(park)) %>%
  addMarkers(data = pdxTrees_parks_sample %>% filter(is.na(nuisance)), group = "Non-Nuisance", lng = ~longitude, lat = ~latitude, popup = ~ paste(park)) %>%
  addLayersControl(
    baseGroups = c("Nuisance", "Non-Nuisance"),
    options = layersControlOptions(collapsed = FALSE)
  )
```
  <!--end-answer-->

