---
chapter: "simulation"
author: ""
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: goldfish-tell-kitchen
---

```{r goldfish-tell-kitchen-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: In this chapter, we considered a simulation where the true jobs number remained constant over time.  Modify the call to the function provided in that example so that the true situation is that there are 15,000 new jobs created every month.  Set your random number seed to the value $1976$.  Summarize what you might conclude from these results as if you were a journalist without a background in data science.


<!--begin-answer-->
```{r nytimes1}
set.seed(1976)
truejobs <- 100
sejobs <- 65
gensamp <- function(truemean = truejobs, truesd = sejobs,
                    nummonths = 12, delta = 15, id = 1) {
  sampyear <- rep(truemean, nummonths) +
    rnorm(nummonths, mean = delta * (1:nummonths), sd = truesd)
  return(data.frame(
    jobsnumber = sampyear,
    month = as.factor(1:nummonths),
    id = id
  ))
}

df <- rbind(
  gensamp(truemean = truejobs, truesd = 0, id = "Truth"),
  gensamp(truemean = truejobs, truesd = sejobs, id = "Sample 1"),
  gensamp(truemean = truejobs, truesd = sejobs, id = "Sample 2"),
  gensamp(truemean = truejobs, truesd = sejobs, id = "Sample 3")
)

ggplot(data = df, aes(x = month, y = jobsnumber)) +
  geom_hline(yintercept = truejobs, linetype = 2) +
  geom_bar(stat = "identity") +
  facet_wrap(~id) +
  ylab("Number of new jobs (in thousands)")
```

One might look at samples 2 or 3 and conclude that job growth is stagnating (though the true pattern is that it is increasing each month).

<!--end-answer-->



