---
chapter: "text"
author: ""
difficulty: "Medium"
date: 2020-06-14 
version: 0.1
tags: [stackexchange, questions, onlineonly]
id: goldfish-sail-sofa
---

```{r goldfish-sail-sofa-default, include = FALSE}
mdsr2exercises::setup()
library(mdsr)
library(tidyverse)
library(httr)
```

TITLE GOES HERE: 

1. The site [stackexchange.com](stackexchange.com) displays questions and answers on technical topics. The following code downloads the most recent R questions related to the `r pkg_macro(dplyr)` package. 

```{r,message=FALSE,eval=FALSE}
library(httr)
# Find the most recent R questions on stackoverflow
getresult <- GET("http://api.stackexchange.com",
  path = "questions",
  query = list(site = "stackoverflow.com", tagged = "dplyr")
)

# Ensure returned without error
stop_for_status(getresult)
```

```{r,include=FALSE}
getresult <- readRDS((paste(system.file("extdata", package = "mdsr2exercises"), "/stackexchangequery.rds", sep = "")))
```

```{r}
questions <- httr::content(getresult) # Grab content
names(questions$items[[1]]) # What does the returned data look like?
length(questions$items)
substr(questions$items[[1]]$title, 1, 68)
substr(questions$items[[2]]$title, 1, 68)
substr(questions$items[[3]]$title, 1, 68)
```

How many questions were returned? Without using jargon, describe in words what is being displayed and how it might be used.

  <!--begin-answer-->

An example query from June 18, 2020:
```{r,message=FALSE}
questions <- httr::content(getresult)
length(questions$items)
```


 <!--end-answer-->
   
2. Repeat the process of downloading the content from [stackexchange.com](stackexchange.com) related to 
the `r pkg_macro(dplyr)` package and summarize the results.   
   
<!--begin-answer-->

Sample answer for June 18 2020 query: 
```{r,message=FALSE, warning = FALSE}
questions <- content(getresult)

query <- questions |>
  purrr::pluck("items") |>
  purrr::map(data.frame, stringsAsFactors = FALSE) |>
  bind_rows() |>
  as_tibble()

query |>
  select(owner.display_name, is_answered, view_count, answer_count, score, title)

query |>
  count(is_answered)

query |>
  summarize(
    avg_reputation = mean(owner.reputation),
    avg_viewcount = mean(view_count),
    avg_answercount = mean(answer_count)
  )
```


<!--end-answer-->


