---
chapter: "dataviz-II"
author: ""
difficulty: "Medium"
date: 2020-07-13 
version: 0.1
tags: [mosaic, facets, ggplot, visualization]
id: kangaroo-win-stove
---

```{r kangaroo-win-stove-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `RailTrail` data set from the `r pkg_macro(mosaicData)` package describes the usage of a rail trail in Western Massachusetts.
Use these data to answer the following questions.
(Hint: For information on how to use faceting and add regression lines, see [*MDSR*, Ch 3.2.2](https://mdsr-book.github.io/mdsr3e/03-datavizII.html#multivariate-displays))

a. Create a scatterplot of the number of crossings per day `volume` against the high temperature that day
b. Separate your plot into facets by `weekday` (an indicator of weekend/holiday vs. weekday)
c. Add regression lines to the two facets

<!--begin-answer-->

```{r }
library(mosaicData)
```

```{r railtrail-1}
ggplot(RailTrail, aes(x = hightemp, y = volume)) +
  geom_point()
```

```{r railtrail-2}
ggplot(RailTrail, aes(x = hightemp, y = volume)) +
  geom_point() +
  facet_wrap(~weekday)
```

```{r railtrail-3, message = FALSE}
ggplot(RailTrail, aes(x = hightemp, y = volume)) +
  geom_point() +
  facet_wrap(~weekday) +
  geom_smooth(method = "lm")
```


<!--end-answer-->
