---
chapter: "join"
author: ""
date: "Second edition"
difficulty: "Easy"
version: 0.1
tags: [first, second, third]
id: kangaroo-iron-saucer
---

(ref:fish-blow-dish) Exercise in file fish-blow-dish

```{r kangaroo-iron-saucer-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Consider the following data frames with information about U.S. states from 1977.

```{r}
statenames <- tibble(names = state.name, twoletter = state.abb)
glimpse(statenames)
statedata <- tibble(
  names = state.name, 
  income = state.x77[, 2], 
  illiteracy = state.x77[, 3]
  )
glimpse(statedata)
```

Create a scatterplot of illiteracy (as a percent of population) and per capita income (in U.S. dollars) with points plus labels of the two letter state abbreviations.  Add a smoother.  Use the `r pkg_macro("ggrepel")` package to offset the names that overlap.  What pattern do you observe?  Are there any outlying observations?

<!--begin-answer-->
```{r message = FALSE}
library(ggrepel)
statemerged <- left_join(
  statenames, 
  statedata, 
  by = "names")
ggplot(statemerged, 
  aes(x = income, y = illiteracy, label = twoletter)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  geom_text_repel() + 
  labs(x = "Per capita income in 1970 ($)", y = "Percent illiterate")
```

For states with lower per capita income in 1977, there seems to be negative relationship between income and illiteracy rates.  Alaska is a notable outlier, likely due to payments provided by the state to all residents through the Alaska Permanent Fund.

<!--end-answer-->

