---
chapter: "algorithmic"
author: ""
difficulty: "Medium"
date: 2020-07-17 
version: 0.1
tags: [functions, babynames]
id: kangaroo-burn-socks
---

```{r kangaroo-burn-socks-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Write a function called `grab_name` that, when given a name and a year as an argument, returns the rows from the `babynames` data frame in the `r pkg_macro(babynames)` package that match that name for that year (and returns an error if that name and year combination does not match any rows).
Run the function once with the arguments `Ezekiel` and `1883` and once with `Ezekiel` and `1983`.

 <!--begin-answer-->
```{r }
library(babynames)
grab_name <- function(x, myyear) {
  result <- babynames %>%
    filter(name == x, year == myyear)
  if (nrow(result) == 0) {
    stop("Name/year combination not found")
  } else {
    return(result)
  }
}
grab_name("Ezekiel", 1883)
grab_name("Ezekiel", 1983)
```

```{r, eval = FALSE}
grab_name("Ezekiel2", 1983) # error message
```

  <!--end-answer-->

