---
chapter: "data-I"
author: ""
date: "First edition"
difficulty: "Easy"
version: 0.1
tags: [baseball, lahman, dplyr, mutate, ggplot, visualization]
id: kid-walk-chair 
---

(ref:kid-walk-chair) Exercise in file kid-walk-chair

```{r kid-walk-chair-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE:   Define two new variables in the `r mdsr2exercises::df_macro(Teams)` data frame in the `r mdsr2exercises::pkg_macro(Lahman)` package. 

a. batting average ($BA$). Batting average is the ratio of hits (`r mdsr2exercises::var_macro(H)`) to at-bats (`r mdsr2exercises::var_macro(AB)`).

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
library(Lahman)
Teams <- mutate(Teams, BA = H / AB)
```
<!--end-answer-->

b. slugging percentage ($SLG$). Slugging percentage is total bases divided by at-bats. To compute total bases, you get 1 for a single, 2 for a double, 3 for a triple, and 4 for a home run.

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
Teams <- mutate(Teams,
  SLG = (H + X2B + 2 * X3B + 3 * HR) / AB
)
```
<!--end-answer-->

c. Plot out the $SLG$ versus `yearID`, showing the individual teams and a smooth curve.

<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
ggplot(Teams, aes(x = yearID, y = SLG)) +
  geom_point() +
  geom_smooth()
```
<!--end-answer-->

d. Same as (c), but plot $BA$ versus year.
<!--begin-answer-->
```{r, message = FALSE, warning = FALSE}
ggplot(Teams, aes(x = yearID, y = BA)) +
  geom_point() +
  geom_smooth()
```
<!--end-answer-->



