---
chapter: "netsci"
author: "Ben Baumer"
difficulty: "Medium"
date: 2020-07-19 
version: 0.1
tags: [airlines, sql, igraph, ggraph, maps, airports]
id: maple-sing-car
---

```{r maple-sing-car-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: The following problem considers the U.S. airport network as a graph.

a. What information do you need to compute the PageRank of the U.S. airport network? Write an SQL query to retrieve this information for 2015. 
(Hint: use the `dbConnect_scidb` function to connect to the `airlines` database.)


 <!--begin-answer-->
```{sql, connection=mdsr::dbConnect_scidb("airlines"), output.var = "E"}
SELECT origin as src, dest, sum(1) as N
FROM flights WHERE year = 2015
GROUP BY origin, dest
```
  <!--end-answer-->

b. Use the data you pulled from SQL and build the network as a *weighted* `tidygraph` object, where the weights are proportional to the frequency of flights between each pair of airports.


 <!--begin-answer-->
```{r message=FALSE}
library(igraph)
g <- graph.data.frame(E, directed = TRUE) |>
  set_edge_attr("weight", value = E(.)$N / sum(E(.)$N))
summary(g)
```
  <!--end-answer-->


c. Compute the PageRank of each airport in your network. What are the top-10 "most central" airports? Where does Oakland International Airport `OAK` rank?

  
 <!--begin-answer-->
```{r }
g <- g |>
  set_vertex_attr("pagerank", value = page_rank(g)$vector)
get.data.frame(g, what = "vertices") |>
  arrange(desc(pagerank)) |>
  head(10)
```
  <!--end-answer-->

d. Update the vertex attributes of your network with the geographic coordinates of each airport (available in the `airports` table). 

 <!--begin-answer-->
```{r warning=FALSE}
vIds <- unique(c(E$src, E$dest))
airports <- tbl(mdsr::dbConnect_scidb("airlines"), "airports")
V <- airports |>
  filter(faa %in% vIds) |>
  collect()
```

```{r }
Vg <- as_data_frame(g, what = "vertices") |>
  mutate(vId = 1:nrow(.))
V <- full_join(x = V, y = Vg, by = c("faa" = "name"))

g <- g |>
  set_vertex_attr("lat", index = V$vId, value = V$lat) |>
  set_vertex_attr("lon", index = V$vId, value = V$lon) |>
  set_vertex_attr("airport", index = V$vId, value = V$name)
```

  <!--end-answer-->

e. Use `ggraph` to draw the airport network. Make the thickness or transparency of each edge proportional to its weight. 


 <!--begin-answer-->
```{r anothermap3,message=FALSE, warning=FALSE, eval=TRUE}
Vg <- get.data.frame(g, what = "vertices")
plot(g,
  layout = layout.kamada.kawai,
  edge.width = 500 * E(g)$weight, edge.color = "dodgerblue",
  edge.curved = TRUE, edge.arrow.size = 0.2, edge.arrow.width = 0.3,
  vertex.label = NA, vertex.size = 100 * V(g)$pagerank,
  vertex.color = "gold"
)
```
  <!--end-answer-->


f. Overlay your airport network on a U.S. map (see the spatial data chapter).

 <!--begin-answer-->
```{r anothermap2,message=FALSE, warning=FALSE}
maps::map("state")
plot(g,
  rescale = FALSE, add = TRUE,
  layout = as.matrix(Vg[, c("lon", "lat")]),
  edge.width = 500 * E(g)$weight, edge.color = "dodgerblue",
  edge.curved = TRUE, edge.arrow.size = 0.2, edge.arrow.width = 0.3,
  vertex.label = NA, vertex.size = 1000 * V(g)$pagerank,
  vertex.color = "gold"
)
```
  <!--end-answer-->


g. Project the map and the airport network using the Lambert Conformal Conic projection.

 <!--begin-answer-->

These plots don't look right here, but they look much better in the RStudio plot window.

```{r anothermap,message=FALSE, warning=FALSE, eval=FALSE}
library(maptools)
library(sp)
data(wrld_simpl)
states <- subset(wrld_simpl, NAME == "United States")
proj <- CRS("+proj=lcc +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")
library(rgdal)
states.proj <- spTransform(states, proj)
summary(g)
V0 <- na.omit(Vg)
coordinates(V0) <- ~ lon + lat
proj4string(V0) <- CRS("+proj=longlat")
summary(V0)
V0.proj <- spTransform(V0, proj)
g0 <- induced.subgraph(g, vids = (!is.na(Vg$lon)))

plot(states.proj)
plot(g0,
  rescale = FALSE, add = TRUE, layout = V0.proj@coords,
  edge.width = 500 * E(g0)$weight, edge.color = "dodgerblue",
  edge.curved = TRUE, edge.arrow.size = 0.2, edge.arrow.width = 0.3,
  vertex.label = NA, vertex.size = 100000000 * V(g0)$pagerank,
  vertex.color = "gold"
)
```
  <!--end-answer-->


h. Crop the map you created to zoom in on your local airport. 

 <!--begin-answer-->
```{r east-coast, eval=FALSE}
plot(states.proj, xlim = c(1000000, 2000000), ylim = c(-600000, 1000000))
plot(g0,
  rescale = FALSE, add = TRUE, layout = V0.proj@coords,
  edge.width = 500 * E(g0)$weight, edge.color = "dodgerblue",
  edge.curved = TRUE, edge.arrow.size = 0.2, edge.arrow.width = 0.3,
  vertex.label = NA, vertex.size = 100000000 * V(g0)$pagerank,
  vertex.color = "gold"
)
```

```{r, include=FALSE}
# needed to clean up namespace
detach("package:igraph", unload = TRUE)
```
  <!--end-answer-->
