---
chapter: "modeling"
author: "Nicholas Horton"
difficulty: "Hard"
date: 2020-09-30 
version: 0.1
tags: [logistic regression, public health, smoking]
id: maple-sleep-sofa
---

```{r maple-sleep-sofa-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Smoking is an important public health concern. Use the `NHANES` data from the `r pkg_macro(NHANES)` package to develop a logistic regression model that identifies predictors of current smoking among those 20 or older. (Hint: note that the `SmokeNow` variable is missing for those who have never smoked: you will need to recode the variable to construct your outcome variable.)

```{r message = FALSE}
library(tidyverse)
library(NHANES)
mosaic::tally(~ SmokeNow + Smoke100, data = filter(NHANES, Age >= 20))
```

 <!--begin-answer-->
Solution welcomed.

```{r}
data <- NHANES %>% 
  mutate(SmokeNow2 = ifelse(SmokeNow == "Yes", 1, 0)) %>% 
  filter(Age >= 20) %>% 
  filter(Poverty != "NA") %>% 
  select(SmokeNow2, Poverty, Age, HomeOwn, Gender)
View(data)

```


 <!--end-answer-->
  
