---
chapter: "data-II"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags:
- baseball
- second
- third
id: monkey-grow-bulb
output: pdf_document
---

(ref:monkey-grow-bulb) Exercise in file monkey-grow-bulb

```{r monkey-grow-bulb-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Consider the number of home runs hit (`r mdsr2exercises::var_macro(HR)`) and home runs allowed (`r mdsr2exercises::var_macro(HRA)`) for the Chicago Cubs ($CHN$) baseball team. Reshape the `r mdsr2exercises::df_macro(Teams)` data from the `r mdsr2exercises::pkg_macro(Lahman)` package into "long" format and plot a time series conditioned on whether the HRs that involved the Cubs were hit by them or allowed by them. 

<!--begin-answer-->
```{r monkey-grow-bulb-1}
library(Lahman)
Teams %>%
  filter(teamID == "CHN") %>%
  select(yearID, HR, HRA) %>%
  pivot_longer(-yearID, names_to = "type", values_to = "home_runs") %>%
  ggplot(aes(x = yearID, y = home_runs, color = type)) +
  geom_point() +
  geom_line()
```

<!--end-answer-->

