---
chapter: "iteration"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [baseball, lahman, dplyr, functions]
id: octopus-choose-table 
depends: girl-catch-room
---

(ref:octopus-choose-table) Exercise in file octopus-choose-table

```{r octopus-choose-table-default, include = FALSE}
mdsr2exercises::setup()
```
TITLE GOES HERE: The team IDs corresponding to Brooklyn baseball teams from the `r mdsr2exercises::df_macro(Teams)` data frame from the `r mdsr2exercises::pkg_macro(Lahman)` package are listed below. Use  `r mdsr2exercises::func_macro(map_int)`  to find the number of seasons in which each of those teams played by calling a function called `count_seasons`.

```{r octopus-choose-table-1, echo = TRUE}
library(Lahman)
bk_teams <- c("BR1", "BR2", "BR3", "BR4", "BRO", "BRP", "BRF")
```

<!--begin-answer-->
```{r octopus-choose-table-2, echo = TRUE}
count_seasons <- function(team) {
  seasons <- Lahman::Teams %>%
    filter(team == teamID) %>%
    nrow()
  return(seasons)
}

map_int(bk_teams, count_seasons)
```
<!--end-answer-->
