---
chapter: "data-I"
author: "Ben Baumer"
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [baseball, lahman, dpylr]
id: owl-freeze-roof 
---

(ref:owl-freeze-roof) Exercise in file owl-freeze-roof

```{r owl-freeze-roof-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: The Major League Baseball Angels have at times been called the California Angels (`r mdsr2exercises::val_macro(CAL)`), the Anaheim Angels (`r mdsr2exercises::val_macro(ANA)`), and the Los Angeles Angels of Anaheim (`r mdsr2exercises::val_macro(LAA)`). Using the `r df_macro(Teams)` data frame in the `r pkg_macro(Lahman)` package: 

a. Find the 10 most successful seasons in Angels history, defining "successful" as the fraction of regular-season games won in the year. In the table you create, include the `yearID`, `teamID`, `lgID`, `W`, `L`, and `WSWin`. See the documentation for `Teams` for the definition of these variables.

<!--begin-answer-->
```{r}
library(Lahman)
Teams %>%
  filter(teamID %in% c("CAL", "ANA", "LAA")) %>%
  dplyr::select(yearID, teamID, lgID, W, L, WSWin) %>%
  mutate(WPct = W / (W + L)) %>%
  arrange(desc(WPct)) %>%
  head(10)
```
<!--end-answer-->

b. Have the Angels ever won the World Series?

<!--begin-answer-->
```{r}
Teams %>%
  filter(teamID %in% c("CAL", "ANA", "LAA")) %>%
  dplyr::select(yearID, teamID, lgID, W, L, WSWin) %>%
  filter(WSWin == "Y")
```
They won the World Series in 2002 as the Anaheim Angels, in their second most successful season in terms of regular-season winning percentage.

<!--end-answer-->

