---
chapter: "join"
author: ""
date: "First edition"
difficulty: "Medium"
version: 0.1
tags: [nycflights13, dplyr, data wrangling]
id: panda-catch-boat 
---


```{r panda-catch-boat-default, include = FALSE}
mdsr2exercises::setup()
```


TITLE GOES HERE: Use the `r pkg_macro("nycflights13")` package and the `r pkg_macro(flights)` and `r pkg_macro(planes)` tables to answer the following questions: 

a. What is the oldest plane (specified by the `tailnum` variable) that flew from New York City airports in 2013?

b. How many airplanes that flew from New York City are included in the `r df_macro(planes)` table?

<!--begin-answer-->
```{r panda-catch-boat-1}
library(nycflights13)
planes2 <- dplyr::select(planes, tailnum, year)
flights2 <- dplyr::select(flights, tailnum)
nyc_flights <- left_join(planes2, flights2) |>
  arrange(year) |>
  unique()
head(nyc_flights)
```

N381AA, manufactured in 1956, is the oldest plane that flew from NYC in 2013.

```{r panda-catch-boat-2}
nyc_flights2 <- distinct(nyc_flights)
nrow(nyc_flights2)
```

There are 3322 unique airplanes.

<!--end-answer-->

