---
chapter: "data-I"
author: "Daniel Kaplan"
date: 2019-10-23 
difficulty: "Medium"
version: 0.1
tags: [nycflights13, dplyr, lubridate, ggplot, visualization]
id: panda-take-bulb 
---

(ref:panda-take-bulb) Exercise in file panda-take-bulb

```{r panda-take-bulb-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Use the `r pkg_macro(nycflights13)` package and the `r df_macro(flights)` data frame to answer the following question: What plane (specified by the `tailnum` variable) traveled the most times from New York City airports in 2013?  Plot the number of trips per week over the year.

<!--begin-answer-->
```{r panda-take-bulb-1, message=FALSE, warning=FALSE}
library(nycflights13)
library(lubridate)
flights |>
  group_by(tailnum) |>
  summarize(count = n()) |>
  arrange(desc(count)) |>
  head()
```

Since NA is not a plane, we see that plane N725MQ had the greatest number of flights, with 575 from NYC airports.

```{r panda-take-bulb-2, message=FALSE, warning=FALSE}
flights2 <- flights |>
  filter(tailnum == "N725MQ") |>
  mutate(week = week(time_hour)) |>
  group_by(week) |>
  summarize(count = n())
ggplot(data = flights2, aes(x = week, y = count)) +
  geom_point() +
  labs(title = "Number of Trips from NYC for Plane N725MQ Each Week")
```

<!--end-answer-->

