---
chapter: "sqlII"
author: ""
difficulty: "Medium"
date: 2020-07-19 
version: 0.1
tags: [lahman, sql, keys]
id: pig-draw-bulb
---

```{r pig-draw-bulb-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: The `Master` table of the `r pkg_macro(Lahman)` database contains biographical information about baseball players. The primary key is the `playerID` variable. There are also variables for `retroID` and `bbrefID`, which correspond to the player's identifier in other baseball databases. Discuss the ramifications of placing a primary, unique, or foreign key on `retroID`.

 <!--begin-answer-->
```{r }
library(Lahman)
glimpse(Master)
```
You can't place a primary key on `retroID`, since a table may only have one primary key. You can (and should) place a unique key on `retroID`, since the values should be unique. You could place a foreign key on `retroID`, but only if there was another table (e.g., the player bio table at (http://www.retrosheet.org)) in which `retroID` corresponded to a primary key.
 <!--end-answer-->


