---
chapter: "algorithmic"
author: ""
difficulty: "Medium"
date: 2020-07-19 
version: 0.1
tags: [first, second, third]
id: pig-hit-ship
---

```{r pig-hit-ship-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Write a function called `prop_cancel` that takes as arguments a month number
and destination airport and returns the proportion of flights missing arrival delay for each day to that destination.
Apply this function to the `nycflights13` package for February and Atlanta airport `ATL` and again with an invalid month number.

 <!--begin-answer-->
```{r, message=FALSE, warning=FALSE }
library(nycflights13)
prop_cancel <- function(monthnum, airport) {
  if (!is.numeric(monthnum)) {
    stop("monthnum must be numeric.\n")
  }
  if (monthnum < 1 | monthnum > 12) {
    stop("monthnum must be between 1 and 12.\n")
  }
  res <- nycflights13::flights %>%
    filter(month == monthnum, dest == airport) %>%
    mutate(missdelay = is.na(arr_delay)) %>%
    group_by(day) %>%
    summarize(count = n(), propmiss = mean(missdelay))
  return(res)
}
prop_cancel(2, "ATL")
```
The second week of 
January, 2013 was a bad time for flights from NYC airports to Atlanta.
```{r, eval = FALSE}

# error message
prop_cancel("ATL", 2)
prop_cancel(22, "ATL")
```

  <!--end-answer-->



