---
chapter: "text"
author: ""
difficulty: "Easy"
date: 2020-06-26 
version: 0.1
tags: [first, second, third]
id: pig-fly-pants
---

```{r pig-fly-pants-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Wikipedia defines a hashtag as "a type of metadata tag used on social networks such as Twitter and other microblogging services, allowing users to apply dynamic, user-generated tagging which makes it possible for others to easily find messages with a specific theme or content." A hashtag must begin with a hash character followed by other characters, and is terminated by a space or end of message. It is always safe to precede the # with a space, and to include letters without diacritics (e.g., accents), digits, and underscores." Provide a regular expression that matches whether a string contains a valid hashtag. 

```{r}
strings <- c(
  "This string has no hashtags",
  "#hashtag city!",
  "This string has a #hashtag",
  "This string has #two #hashtags"
)
```

  <!--begin-answer-->
```{r, eval=FALSE}
grep(strings, pattern = "#[A-Za-z0-9]")
```

  <!--end-answer-->
