---
chapter: "learning-II"
author: ""
difficulty: "Medium"
date: 2020-07-15 
version: 0.1
tags: [baseball, lahman, clustering]
id: pig-wear-table
---

```{r pig-wear-table-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Perform the clustering on *pitchers* who have been elected to the Hall of Fame using the `Pitching` dataset in the `Lahman` package. Use wins (`W`), strikeouts (`SO`), and saves (`SV`) as criteria. 

<!--begin-answer-->
```{r message=FALSE}
library(Lahman)
hof <- Pitching %>%
  group_by(playerID) %>%
  inner_join(HallOfFame, by = c("playerID" = "playerID")) %>%
  filter(inducted == "Y" & votedBy == "BBWAA") %>%
  summarize(tW = sum(W), tSO = sum(SO), tSV = sum(SV)) %>%
  filter(tSO > 500)
```

Here the clusters are very distinct and seems to be based entirely on strikeouts. Note that only a handful of pitchers in the Hall of Fame have accumualated many saves, and that the clustering algorithm did not group them together. 

```{r ex-hof-cluster2}
clusts <- hof %>%
  select(-playerID) %>%
  kmeans(centers = 3) %>%
  fitted("classes")
hof <- hof %>%
  mutate(cluster = clusts) %>%
  arrange(desc(clusts))
ggplot(data = hof, aes(x = tW, y = tSO, size = tSV, color = factor(cluster))) +
  geom_point()
```
<!--end-answer-->


