---
chapter: "learning-I"
author: ""
difficulty: "Medium"
date: 2020-07-14 
version: 0.1
tags: [first, second, third]
id: pollen-show-map
---

```{r pollen-show-map-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: The `nasaweather` package contains data about tropical `storms` from 1995--2005. Consider the scatterplot between the `wind` speed and `pressure` of these `storms` shown below.

```{r storms, message=FALSE, fig.height = 3}
library(mdsr)
library(nasaweather)
ggplot(data = storms, aes(x = pressure, y = wind, color = type)) +
  geom_point(alpha = 0.5)
```

The `type` of storm is present in the data, and four types are given: extratropical, hurricane, tropical depression, and tropical storm. There are [complicated and not terribly precise definitions](https://en.wikipedia.org/wiki/Tropical_cyclone#Classifications.2C_terminology.2C_and_naming) for storm type. Build a classifier for the `type` of each storm as a function of its `wind` speed and `pressure`.  

Why would a decision tree make a particularly good classifier for these data?
Visualize your classifier in the data space.

  <!--begin-answer-->
```{r }
library(rpart)
rpart(type ~ wind + pressure, data = storms)
```
  <!--end-answer-->
