---
chapter: "dataviz-II"
author: "Ben Baumer"
difficulty: "Easy"
date: 2020-08-11 
version: 0.1
tags: [first, second, onlineonly]
id: rabbit-lay-fork
---

```{r rabbit-lay-fork-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: LEDECKY: Consider the following data graphic about world-class swimmers. Emphasis is on [Katie Ledecky](https://en.wikipedia.org/wiki/Katie\_Ledecky), a five-time Olympic gold medalist. It may be helpful to peruse the original article, entitled "[Katie Ledecky Is The Present And The Future Of Swimming](https://fivethirtyeight.com/features/katie-ledecky-is-the-present-and-the-future-of-swimming/)".

```{r echo=FALSE}
knitr::include_graphics(paste(system.file("extdata", package = "mdsr2exercises"), "/ledecky.png", sep = ""))
```

Suppose that the graphic was generated from a data frame like the one shown below (it wasn't---these are fake data). 

```{r, echo=FALSE}
tibble::tribble(
  ~name, ~gender, ~distance, ~time_in_sd,
  "Ledecky", "F", 100, -0.8,
  "Ledecky", "F", 200, 1.7,
  "Ledecky", "F", 400, 2.9
)
```

Note: Recall that [*standard deviation*](https://en.wikipedia.org/wiki/Standard_deviation) is a measure of the spread of a set of numbers. In this case, a time that is +1 standard deviation *above* the mean is *faster* than the average time (among the top 50 times).

1. What variable is mapped to the position aesthetic in the horizontal direction? 
1. What variable is mapped to the color aesthetic in the vertical direction?
1. What variable is mapped to the position aesthetic in the vertical direction?

<!--answer-start-->
1. `distance`
1. `time_in_sd`
1. `gender`
<!--answer-end-->



