---
chapter: "data-I"
author: "Daniel Kaplan"
difficulty: "Hard"
date: 2019-10-24 
version: 0.1
tags: [first, second, onlineonly]
id: rat-win-sheet 
---

(ref:rat-win-sheet) Exercise in file rat-win-sheet

```{r rat-win-sheet-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Replicate the wrangling to create the `house_elections` table in the `r pkg_macro(fec)` package from the original Excel source file.


<!--begin-answer-->
See, for example, <http://classic.fec.gov/pubrec/fe2012/federalelections2012.xls> for the Excel workbook. The most up-to-date data wrangling code can be found in the `r mdsr2exercises::pkg_macro(fec)` GitHub repository (<https://github.com/beanumber/fec/blob/master/R/etl_extract.R>). Here we have pasted the code as of this writing.

```{r rat-win-sheet-1, echo = TRUE, eval=FALSE}
sheets <- readxl::excel_sheets(src)
house_sheet <- grep("House Results", x = sheets)
elections <- readxl::read_excel(src, sheet = house_sheet)
names(elections) <- names(elections) %>%
  tolower() %>%
  gsub(" ", "_", x = .) %>%
  gsub("#", "", x = .) %>%
  gsub("%", "pct", x = .)
house_elections <- elections %>%
  dplyr::filter_(~ fec_id != "n/a", ~ d != "S") %>%
  dplyr::rename_(
    district = ~d, incumbent = ~`(i)`,
    general_votes = ~general_votes_
  ) %>%
  dplyr::select_(
    ~state_abbreviation, ~district, ~fec_id, ~incumbent,
    ~candidate_name, ~party, ~primary_votes, ~runoff_votes,
    ~general_votes, ~ge_winner_indicator
  ) %>%
  dplyr::mutate_(
    primary_votes = ~ readr::parse_number(primary_votes),
    district = ~ trimws(district),
    is_incumbent = ~ incumbent == "(I)"
  ) %>%
  dplyr::group_by_(~fec_id) %>%
  dplyr::summarize_(
    state = ~ max(state_abbreviation),
    district = ~ max(district),
    incumbent = ~ sum(is_incumbent, na.rm = TRUE) > 0,
    name = ~ max(candidate_name),
    party = ~ ifelse("R" %in% party, "R",
      ifelse("D" %in% party, "D", max(party))
    ),
    primary_votes = ~ sum(primary_votes, na.rm = TRUE),
    runoff_votes = ~ sum(runoff_votes, na.rm = TRUE),
    general_votes = ~ sum(general_votes, na.rm = TRUE),
    ge_winner = ~ max(ge_winner_indicator, na.rm = TRUE)
  )
```
<!--end-answer-->
