---
chapter: "sqlI"
author: ""
difficulty: "Hard"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: seal-lend-glasses
---

```{r seal-lend-glasses-default, include = FALSE}
mdsr2exercises::setup()
library(tidyverse)
```

TITLE GOES HERE: The following open-ended question may require more than one query and a thoughtful response.
Based on data from 2012 only, and assuming that transportation to the airport is not an issue, would you rather fly out of JFK, LaGuardia (LGA), or Newark (EWR)? Why or why not? 
Use the `dbConnect_scidb` function to connect to the `airlines` database.

<!--begin-answer-->
An extremely simplistic solution would just compare the average flight delays and proportion of flights that were canceled.
```{r, warning = FALSE, message= FALSE}
library(RMySQL)
con <- mdsr::dbConnect_scidb(dbname = "airlines")

myquery <- 'SELECT 
  MAX(origin) as airport,
  sum(1) as numFlights, 
  sum(cancelled) as numCancelled,
  avg(cancelled) as pctCancelled,
  avg(arr_delay) as avgdelay
FROM flights o
WHERE year = 2012 
  AND origin IN ("JFK", "LGA", "EWR")
GROUP BY origin
ORDER BY pctCancelled;'

dbGetQuery(con, myquery)
```

A more sophisticated analysis (left to the reader) would be to account for differences in carriers and destinations (since the airports have very different patterns of flights).  

<!--end-answer-->



