---
chapter: "sqlI"
author: ""
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: seaweed-cut-knob
---

```{r seaweed-cut-knob-default, include = FALSE}
library(tidyverse)
library(mdsr)
mdsr2exercises::setup()
```

TITLE GOES HERE: The following questions require use of the `r pkg_macro(Lahman)` package and reference basic baseball terminology. (See https://en.wikipedia.org/wiki/Baseball_statistics for explanations of any acronyms.) 


a. List the names of all batters who have at least 300 home runs (HR) and 300 stolen bases (SB) in their careers and rank them by career batting average ($H/AB$). 


<!--begin-answer-->

Connection to database:
```{r}
library(RMySQL)
con <- mdsr::dbConnect_scidb(dbname = "lahman")
```

```{r}
library(RMySQL)

myquery <- "SELECT concat(namelast, ',', namefirst) as name, 
            sum(hr) as tHR, sum(sb) as tSB, 
            sum(h) / sum(ab) as BAvg
          FROM Batting b
          LEFT JOIN Master m ON b.playerid = m.playerid
          GROUP BY b.playerid
          HAVING tHR >= 300 AND tSB >= 300
          ORDER BY BAvg desc LIMIT 0,6;"


dbGetQuery(con, myquery)
```
  
<!--end-answer-->
 

b. List the names of all pitchers who have at least 300 wins (W) and 3,000 strikeouts (SO) in their careers and rank them by career winning percentage ($W/(W+L)$). 


<!--begin-answer-->
  
```{r }
library(RMySQL)


myquery <- "
SELECT concat(namelast, ', ', namefirst) as name, 
  sum(w) as tW, sum(so) as tSO, 
  sum(w) / sum(w+l) as WPct
FROM Pitching p
LEFT JOIN Master m ON p.playerid = m.playerid
GROUP BY p.playerid
HAVING tW >= 300 AND tSO >= 3000
ORDER BY WPct desc
LIMIT 0,6;"

dbGetQuery(con, myquery)
```
<!--end-answer-->


c. The attainment of either 500 home runs (HR) or 3,000 hits (H) in a career is considered to be among the greatest achievements to which a batter can aspire. These milestones are thought to guarantee induction into the Baseball Hall of Fame, and yet several players who have attained either milestone have not been inducted into the Hall of Fame. Identify them. 


<!--begin-answer-->
```{r}
library(RMySQL)

myquery <- "
SELECT Name, tHR, tH, is_inducted 
FROM
  (SELECT m.playerID, 
          concat(namelast, ' ', namefirst) as Name,
          sum(hr) as tHR, sum(h) as tH
   FROM Batting b
   JOIN Master m ON m.playerID = b.playerID
   GROUP BY b.playerID
   HAVING tHR >= 500 OR tH >= 3000) as bg
LEFT JOIN 
  (SELECT h.playerID,
          sum(if(inducted = 'Y', 1, 0)) as is_inducted
   FROM HallOfFame h
   GROUP BY h.playerID) as hof 
ON hof.playerID = bg.playerID
WHERE is_inducted < 1;"

dbGetQuery(con, myquery)
```

Craig Biggio was inducted into the Hall of Fame in 2015. Pete Rose was banned from baseball in 1989, and the candidacies of the other four players are compromised by their alleged (or confirmed) steroid use. 


<!--end-answer-->



