---
chapter: "learning-II"
author: ""
difficulty: "Medium"
date: 2020-07-14 
version: 0.1
tags: [first, second, third]
id: shark-make-fork
---

```{r shark-make-fork-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
library(mdsr)
```

TITLE GOES HERE: Consider the $k$-means clustering algorithm applied to the BigCities data.
Would you expect to obtain different results if the location coordinates were *projected* (see the "Working with spatial data" chapter)?  


<!--begin-answer-->
Possibly, but not necessarily. It depends on how grossly the coordinates are distorted from one projection to the next. Here we use a [Cassini projection](https://en.wikipedia.org/wiki/Cassini_projection) to produce a different set of coordinates. The clustering algorithm still basically picks up on the continents in the same way, even though the map looks quite different. 

```{r message=FALSE}
BigCities <- world_cities %>%
  arrange(desc(population)) %>%
  head(4000) %>%
  select(longitude, latitude)

```

```{r message=FALSE}
library(sp)
coordinates(BigCities) <- ~ longitude + latitude
proj4string(BigCities) <- CRS("+proj=longlat")
BigCities_proj <- BigCities %>%
  spTransform(CRS("+proj=cass +lon_0=12.4521272222222 +lat_0=41.9244030555555 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
```

```{r cluster-cities-projected, message=FALSE}
set.seed(15)
library(mclust)
city_clusts <- BigCities_proj %>%
  coordinates() %>%
  kmeans(centers = 6) %>%
  fitted("classes") %>%
  as.character()
big_clusters <- BigCities_proj %>%
  as_tibble() %>%
  mutate(cluster = city_clusts)
ggplot(data = big_clusters, aes(x = longitude, y = latitude)) +
  geom_point(aes(color = cluster), alpha = 0.5)
```
<!--end-answer-->


