---
chapter: "learning-II"
author: ""
difficulty: "Medium"
date: 2020-07-14 
version: 0.1
tags: [kmeans, clustering, bigcities, projection]
id: shark-make-fork
---

```{r shark-make-fork-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Consider the $k$-means clustering algorithm applied to the `BigCities` data.
Would you expect to obtain different results if the location coordinates were *projected* (see the "Working with spatial data" chapter)?  


<!--begin-answer-->
Possibly, but not necessarily. It depends on how grossly the coordinates are distorted from one projection to the next. Here we use a [Cassini projection](https://en.wikipedia.org/wiki/Cassini_projection) to produce a different set of coordinates. The clustering algorithm still basically picks up on the continents in the same way, even though the map looks quite different. 

```{r message=FALSE}
BigCities <- world_cities |>
  arrange(desc(population)) |>
  head(4000) |>
  select(longitude, latitude)
```

```{r message=FALSE}
library(sf)
BigCities_proj <- BigCities |>
  st_as_sf(coords = c("longitude", "latitude")) |>
  st_set_crs(4326) |>
  st_transform("+proj=cass +lon_0=12.4521272222222 +lat_0=41.9244030555555 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs")
```

```{r cluster-cities-projected, message=FALSE}
set.seed(15)
city_clusts <- BigCities_proj |>
  st_coordinates() |>
  kmeans(centers = 6) |>
  fitted("classes") |>
  as.character()
big_clusters <- BigCities_proj |>
  mutate(cluster = city_clusts)
ggplot(data = big_clusters) +
  geom_sf(aes(color = cluster), alpha = 0.5)
```
<!--end-answer-->


