---
chapter: "dataviz-II"
author: ""
difficulty: "Medium"
date: 2020-07-13 
version: 0.1
tags: [multivariate, palmerpenguins, ggplot, visualization, facets]
id: snake-forgive-pan
---

```{r snake-forgive-pan-default, include = FALSE}
mdsr2exercises::setup()
```


TITLE GOES HERE: Using the `penguins` data set from the `r pkg_macro(palmerpenguins)` package:


a. Create a scatterplot of `bill_length_mm` against `bill_depth_mm` where individual species are colored and a regression line is added to each species. 
What do you observe about the association of bill depth and bill length?

<!--begin-answer-->

```{r ggyaGalton}
library(palmerpenguins)
```

```{r ggyaGalton2-ex, message = FALSE, warning = FALSE}
ggplot(data = penguins, aes(x = bill_depth_mm, y = bill_length_mm)) +
  labs(x = "Bill depth (mm)", y = "Bill length (mm)") +
  geom_point() +
  facet_grid(~sex) +
  geom_smooth(method = "lm")
```



<!--end-answer-->

b. Repeat the same scatterplot but now separate your plot into facets by `species`.
Add regression lines to all of your facets.
How would you summarize the association between bill depth and bill length.

<!--begin-answer-->

```{r ggyaGalton3-ex, warning = FALSE, message = FALSE}
ggplot(
  data = penguins, 
  aes(x = bill_depth_mm, y = bill_length_mm, colour = sex)
) +
  labs(x = "Bill depth (mm)", y = "Bill length (mm)") +
  geom_point() +
  facet_grid(~species) +
  geom_smooth(method = "lm")
```



<!--end-answer-->



