---
chapter: "simulation"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: spider-cut-plant
---

```{r spider-cut-plant-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: What is the impact if the residuals from a linear regression model are skewed (and not from a normal distribution)?

Repeatedly generate data from a "true" model given by:
```{r }
n <- 250
rmse <- 1
x1 <- rep(c(0, 1), each = n / 2) # x1 resembles 0 0 0 ... 1 1 1
x2 <- runif(n, min = 0, max = 5)
beta0 <- -1
beta1 <- 0.5
beta2 <- 1.5
y <- beta0 + beta1 * x1 + beta2 * x2 + rexp(n, rate = 1 / 2)
```

For each simulation, fit the linear regression model and display the distribution of 1,000 estimates of the $\beta_1$ parameter (note that you need to generate the vector of outcomes each time).

<!--begin-answer-->

```{r plotexp}
mosaic::plotDist("exp", rate = 1 / 2)
```

We can see that the distribution of the residuals is skewed.


```{r }
set.seed(1899)
```

```{r dosimhist1}
dosim <- function() {
  y <- beta0 + beta1 * x1 + beta2 * x2 +
    rexp(n, rate = 1 / 2)
  mod <- lm(y ~ x1 + x2)
  result <- coef(mod)[2]
  return(result) # coefficient for X1
}
res <- map_dbl(1:1000, ~dosim()) %>%
  enframe(value = "x1")

res %>%
  skim(x1)

ggplot(data = res, aes(x = x1)) +
  geom_density() +
  stat_function(
    fun = dnorm, args = list(mean = mean(res$x1), sd = sd(res$x1)),
    linetype = 2
  ) +
  ggtitle("distribution of regression parameter") +
  scale_x_continuous("beta 1 coefficients")
```

While there is some deviation from the normal distribution, the normal approximation works effectively when the residuals come from an exponential (skewed) distribution).  This is not unexpected given that the 
central limit theorem holds since the sample size is sufficiently large.

<!--end-answer-->


