---
chapter: "regression"
author: ""
difficulty: "Easy"
date: 2020-07-16 
version: 0.1
tags: [first, second, third]
id: spider-keep-bottle
---

```{r spider-keep-bottle-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: In 1966, [Cyril Burt](http://en.wikipedia.org/wiki/Cyril_Burt) published a paper called *The genetic determination of differences in intelligence: A study of monozygotic twins reared apart.* The data consist of IQ scores for [an assumed random sample of] 27 identical twins, one raised by foster parents, the other by the biological parents. 

Here is the regression output for using `Biological` IQ to predict `Foster` IQ:

```{r message=FALSE, eval=TRUE}
library(mdsr)
library(faraway)
mod <- lm(Foster ~ Biological, data = twins)
coef(mod)
mosaic::rsquared(mod)
```
Which of the following is **FALSE**? Justify your answers.

-  Alice and Beth were raised by their biological parents. If Beth's IQ is 10 points higher than Alice's, then we would expect that her foster twin Bernice's IQ is 9 points higher than the IQ of Alice's foster twin Ashley. 
-  Roughly 78% of the foster twins' IQs can be accurately predicted by the model.
-  The linear model is $\widehat{Foster} = 9.2 + 0.9 \times Biological$.
-  Foster twins with IQs higher than average are expected to have biological twins with higher than average IQs as well.

 <!--begin-answer-->

-  TRUE
-  FALSE: that is not a correct interpretation of the $R^2$ value.
-  TRUE
-  TRUE

<!--end-answer-->


