---
chapter: "simulation"
author: "Nicholas Horton"
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: squirrel-cost-mug
---

```{r squirrel-cost-mug-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: What is the impact of the violation of the equal variance
assumption for linear regression models?  Repeatedly generate data from a "true" model given by the following code.
```{r }
n <- 250
rmse <- 1
x1 <- rep(c(0, 1), each = n / 2) # x1 resembles 0 0 0 ... 1 1 1
x2 <- runif(n, min = 0, max = 5)
beta0 <- -1
beta1 <- 0.5
beta2 <- 1.5
y <- beta0 + beta1 * x1 + beta2 * x2 + rnorm(n, mean = 0, sd = rmse + x2)
```
For each simulation, fit the linear regression model and display the distribution of 1,000 estimates of the $\beta_1$ parameter (note that you need to generate the vector of outcomes each time).  Does the distribution of the parameter follow a normal distribution?

<!--begin-answer-->


```{r }
set.seed(1899)
```

```{r dosimhist2}
dosim <- function() {
  y <- beta0 + beta1 * x1 + beta2 * x2 +
    rnorm(n, mean = 0, sd = rmse + x2)
  mod <- lm(y ~ x1 + x2)
  result <- coef(mod)[2]
  return(result) # coefficient for X1
}
res <- map_dbl(1:1000, ~dosim()) %>%
  enframe(value = "x1")

res %>%
  skim(x1)

ggplot(data = res, aes(x = x1)) +
  geom_density() +
  stat_function(
    fun = dnorm, args = list(mean = mean(res$x1), sd = sd(res$x1)),
    linetype = 2
  ) +
  ggtitle("distribution of regression parameter") +
  scale_x_continuous("beta 1 coefficients")
```

While there is some deviation from the normal distribution (and slightly heaver tails), the normal approximation still works fairly effectively in this example.

<!--end-answer-->


