---
chapter: "simulation"
author: ""
difficulty: "Medium"
date: 2020-07-20 
version: 0.1
tags: [first, second, third]
id: tiger-give-door
---

```{r tiger-give-door-default, include = FALSE}
mdsr2exercises::setup()
```

TITLE GOES HERE: Generate $n=5,000$ observations from a logistic regression model with parameters 
intercept $\beta_0=-1$, slope $\beta_1=0.5$, and distribution of the predictor being normal with mean 1 and standard deviation 1. Calculate and interpret the resulting parameter estimates and confidence intervals.


<!--begin-answer-->
```{r, message= FALSE }
intercept <- -1
beta <- 0.5
n <- 5000
xtest <- rnorm(n, mean = 1, sd = 1)
linpred <- intercept + (xtest * beta)
prob <- exp(linpred) / (1 + exp(linpred))
ytest <- ifelse(runif(n) < prob, 1, 0)
logreg <- glm(ytest ~ xtest, family = binomial)
coef(logreg)
exp(coef(logreg))
confint(logreg)
exp(confint(logreg))
```    

We see that the true parameters have been recovered (our estimates differ only slightly).

<!--end-answer-->


