---
chapter: "text"
author: ""
difficulty: "Medium"
date: 2020-06-14 
version: 0.1
tags: [first, second, onlineonly]
id: walnut-see-table
---

```{r walnut-see-table-default, include = FALSE}
mdsr2exercises::setup()
library(mdsr)
library(tidyverse)
library(ggplot2)
```

TITLE GOES HERE: 

a. Use regular expressions to determine the number of speaking lines [The Complete Works of William Shakespeare](http://www.gutenberg.org/cache/epub/100/pg100.txt). Here, we care only about how many times a character speaks---not what they say or for how long they speak. 

<!--
% XX NH need to fix this by making the data available.
-->
 
<!--begin-answer-->
```{r,message=FALSE, warning = FALSE}
shakespeare <- readRDS(paste(system.file("extdata", package = "mdsr2exercises"), "/Shakespeare.Rds", sep = ""))

length(shakespeare)
speaker_lines <- grep("^  [A-Z ]+\\.", shakespeare)
length(speaker_lines)
```

<!--end-answer-->
  

b. Make a bar chart displaying the top 100 characters with the greatest number of lines. **Hint** you may want to use either the `stringr::str_extract` or `strsplit` function here.
  
<!--begin-answer-->
Here are two different ways to get the list of speakers:
```{r,message=FALSE}
speakers <- str_extract(shakespeare, "^  [A-Z ]+\\.")

words <- unlist(strsplit(shakespeare, "\\. "))
speakers <- words[grep("^  [A-Z ]+$", words)]

speaker_df <- speakers %>%
  data.frame(speaker = .) %>%
  filter(!is.na(speaker)) %>%
  group_by(speaker) %>%
  summarize(N = n()) %>%
  arrange(desc(N)) %>%
  head(100)
ggplot(data = speaker_df, aes(x = reorder(speaker, N), y = N)) +
  geom_bar(stat = "identity") +
  coord_flip()
```

 
 <!--end-answer-->
 
3. In this problem, you will do much of the work to recreate Mark Hansen's *Shakespeare Machine*. Start by watching a [video clip](http://vimeo.com/54858820) of the exhibit. Use *The Complete Works of William Shakespeare* and regular expressions to find all of the hyphenated words in Shakespeare Machine. How many are there? Use `\%in\%` to verify that your list contains the following hyphenated words pictured at 00:46 of the clip.

<!--begin-answer-->
```{r}
hyphenated <- shakespeare[grep(" [a-z]+-[a-z,']+( |\\.|\\,|-)", shakespeare)]
words <- unlist(strsplit(hyphenated, " "))
res <- words[grep("-", words)]
length(res)

sm_words <- c(
  "true-fix'd", "pale-hearted", "lean-fac'd", "hard-hearted",
  "best-regarded", "thick-ribbed", "both-sides", "sea-like.",
  "shrill-shrieking", "lust-stain'd", "tragical-historical,"
)
sm_words %in% res
```

 <!--end-answer-->


