---
chapter: "regression"
author: ""
difficulty: "Medium"
date: 2020-07-16 
version: 0.1
tags: [first, second, third]
id: wolf-rise-rug
---

```{r wolf-rise-rug-default, include = FALSE}
library(tidyverse)
mdsr2exercises::setup()
```

TITLE GOES HERE: Investigators in the HELP (Health Evaluation and Linkage to Primary Care) study were interested in modeling predictors of being `homeless` (one or more nights spent on the street or in a shelter in the past six months vs. housed) using baseline data from the clinical trial.  Fit and interpret a parsimonious model that would help the investigators identify predictors of homelessness.

 <!--begin-answer-->
Answers may vary.  Consider the following.

```{r }
library(mdsr)
logreg <- glm(homeless == "homeless" ~ sex + substance + pcs + mcs,
  family = binomial, data = HELPrct
)
msummary(logreg)
exp(coef(logreg))
```
We see that males have 78% higher odds of homelessness than females (controlling for other factors).  Similarly, cocaine-involved and heroin-involved subjects have lower odds than alcohol-involved subjects.  For every additional physical component score (PCS) value, odds of homelessless go down by 2% (controlling for other factors).


<!--end-answer-->


